### 2016-09-14 paper.tex
Added template and basic files

\documentclass{llncs}
\usepackage{graphics}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage[dvips]{epsfig}
\usepackage[latin1]{inputenc}
\usepackage{url}

\def\CC{{C\hspace{-.05em}\raisebox{.4ex}{\tiny\bf ++}}~}
\addtolength{\textfloatsep}{-0.5cm}
\addtolength{\intextsep}{-0.5cm}

%%%%%%%%%%%%%%%% Titulo %%%%%%%%%%%%%%%
\title{Predicting Levels of Sales for Newly Published Books using Cost-Sensitive Ensemble Methods}

%%%%%%%%%%%%%%%% autores %%%%%%%%%%%%%%
\author {}
\institute{}
% Antonio - Hossam add your 'official' e-mail here. ;)

\date{}

\begin{document}
\maketitle

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}

\end{abstract}

%********************************************************************************

\section{Introduction}

\section{Materials and methods}
\subsection{Basic classifiers}

In order to show the need for more intelligent and complex classification models, basic and more common models are experimented and applied first. 
\begin{itemize}

\item \textbf{$k$-Nearest Neighbors ($k$-NN)}

\item \textbf{Naive Bayes classifier}

\item \textbf{C4.5 Decision Trees}

\item \textbf{Multilayer Perceptron neural networks (MLP)}

\item \textbf{Support Vector Machines (SVM)}

\end{itemize}

\subsection{Ensemble classifiers}

\begin{itemize}
\item \textbf{Bagging}
\item \textbf{Boosting}
\item \textbf{Random Forest}
\end{itemize}

\section{Cost sensitive classification}

\subsection{Cost sensitive learning}
\subsection{Cost sensitive classification}

\section{Dataset description}

The obtained dataset contains collected information about 6083 different books produced by 209 publishers. Each book in the dataset is represented by 10 feature as shown in Table \ref{tabla:params_pre_sales}.

\begin{table}
\caption{Pre-sales features and Sales level(Output class). } 
\label{tabla:params_pre_sales}
\begin{center}
\begin{tabular}{|c|l|l|c|c|}
\hline 
No. & Feature Name & Variable & Type & In/Out\\
\hline 
1 & retail price (when launched) & \texttt{ret\_price} & numerical & input\\
2 & main subject (code) & \texttt{subject1} & numerical & input\\
3 & bookbinding (code) & \texttt{binding} & categorical & input\\
4 & gifts (promotional books) & \texttt{gifts} & numerical & input\\
5 & units distributed as novelty & \texttt{distrib\_novelty} & numerical & input\\
6 & total number of points of sale & \texttt{tot\_points\_sale} & numerical & input\\
7 & total number of points of sale (1st year) & \texttt{tot\_points\_sale\_1st\_year} & numerical & input\\
8 & weeks on sale & \texttt{weeks\_sale} & numerical & input\\
9 & print run & \texttt{print\_run} & numerical & input\\
\hline 
\hline
10 & Sales level & \texttt{sales\_level} & categorical & output\\
\hline 
\end{tabular}
\end{center}
\end{table}

The output variable which is the total sales is a categorical variable the represent the level of the quantity sold of a given book. Four categories are used to represent the total sales level: Low (L), Medium (M), High (H) and Very High (VH). Table \ref{table:freq} shows the ranges of total sales that correspond to each category along with the number of sold books that fall in.

Table \ref{table:freq} and Figure \ref{fig:count} reveal more information about the nature of the dataset. We can notice that most of 77\% of the boos investigated are categorized as VL and L with limited number of sales. On the other side, the books that achieved more than 2000 sold copies are just around 4\%. This makes the problem of identifying those two categories much harder. The new categorical feature is used to replace the old numerical Total Sales feature in the GP classification case.

\begin{table*}[ht]
\caption{Categories corresponding to total sales }
\centering{}%
\begin{tabular}{|c|c|c|c|}
\hline 
Category & Range of total sales & Count & Ratio\tabularnewline
\hline 
\hline 
Low & 0-60 & 1631 & 26.8\%\tabularnewline
\hline 
Medium & 61-300 & 2212 & 36.4\%\tabularnewline
\hline 
High & 300-1000 & 1460 & 24\%\tabularnewline
\hline 
Very High & $>$1000 & 780 & 12.8\%\tabularnewline
\hline 
\end{tabular}
\label{table:freq}
\end{table*}

\section{Evaluation measurements}

To evaluate the developed classification models, first, we refer the confusion matrix shown in Table \ref{fig:confusionmatrix} which is considered as a basic source for evaluating any binary classification model. In our case which is a multiclass prediction problem, this matrix can be expanded with a row and column for each class to evaluate the multiclass classfication models. Three measurements are used to evaluate the applied classifiers: accuracy rate, precision and recall. The accuracy rate simply measures the total number of correctly classified instances over the total number of instances $N$ as shown in Equation \ref{equation:acc}.

Precision is the ratio of the correctly classified instances as $i$ to the number of instances classified as $i$. On the other side, recall is the ratio of the correctly classified instances as $i$ to the number of actual $i$ instances . Precision and recall are given in Equation \ref{equation:precision} and \ref{equation:recall}, respectively.

\begin{figure*}[ht]
\begin{center}
\includegraphics[scale=0.50]{confusion-matrix}
\end{center}
\caption{Basic confusion matrix.}
\label{fig:confusionmatrix}
\end{figure*}

\begin{equation}
Accuracy=\frac{\sum_{i}C_{ii}}{N}
\label{equation:acc}
\end{equation}

\begin{equation}
Precision_{i}=\frac{C_{ii}}{\sum_{j}C_{ij}}
\label{equation:precision}
\end{equation}

\begin{equation}
Recall_{i}=\frac{C_{ii}}{\sum_{j}C_{ji}}
\label{equation:recall}
\end{equation}

\begin{figure*}[ht]
\begin{center}
\includegraphics[scale=0.40]{Confusion-matrix-multiclass-default}
\end{center}
\caption{Default cost matrix.}
\label{fig:count}
\end{figure*}

\section{Experiments and results}

%This is just the first step of the experiments
% This table shows the average results of 10X10-folds experiments of the basic classifiers.
% It is impossible to calculate directly the average Precision and Recall for each class for multiclass problems in Weka Experimenter. So I have written a bash script to generate the row predictions utilizing Weka 3.9 developers version. Then I wrote another Python script to process these predicitons and calculate the precision and recall measurements as listed in this table.

\begin{table}
\caption{Classification results using basic classifiers (without print-run)}
\centering{}%
\begin{tabular}{|c|c|c|c|c|c|}
\hline 
 & kNN  & NB  & J48  & MLP  & SVM\tabularnewline
\hline 
\hline 
$Accuracy$  & 0.69$\pm$0.0026 & 0.67$\pm$0.0008 & 0.7$\pm$0.004 & 0.71$\pm$0.0027 & 0.67$\pm$0.0012\tabularnewline
\hline 
\hline 
$Recall_{L}$  & 0.75$\pm$0.0044 & 0.86$\pm$0.0013 & 0.79$\pm$0.0071 & 0.78$\pm$0.0222 & 0.59$\pm$0.0035\tabularnewline
\hline 
$Precision_{L}$  & 0.78$\pm$0.003 & 0.73$\pm$0.0017 & 0.8$\pm$0.0049 & 0.8$\pm$0.0173 & 0.84$\pm$0.0025\tabularnewline
\hline 
\hline 
$Recall_{M}$  & 0.74$\pm$0.0034 & 0.66$\pm$0.0024 & 0.7$\pm$0.0072 & 0.71$\pm$0.0129 & 0.82$\pm$0.002\tabularnewline
\hline 
$Precision_{M}$  & 0.65$\pm$0.003 & 0.64$\pm$0.0007 & 0.68$\pm$0.0079 & 0.69$\pm$0.007 & 0.59$\pm$0.0012\tabularnewline
\hline 
\hline 
$Recall_{H}$  & 0.59$\pm$0.0047 & 0.53$\pm$0.0022 & 0.6$\pm$0.0099 & 0.65$\pm$0.0346 & 0.55$\pm$0.0016\tabularnewline
\hline 
$Precision_{H}$  & 0.62$\pm$0.0037 & 0.58$\pm$0.0017 & 0.62$\pm$0.0058 & 0.62$\pm$0.0109 & 0.63$\pm$0.0012\tabularnewline
\hline 
\hline 
$Recall_{VH}$  & 0.6$\pm$0.0073 & 0.53$\pm$0.003 & 0.72$\pm$0.0086 & 0.68$\pm$0.0336 & 0.61$\pm$0.0012\tabularnewline
\hline 
$Precision_{VH}$  & 0.79$\pm$0.0071 & 0.81$\pm$0.0032 & 0.74$\pm$0.0072 & 0.77$\pm$0.0212 & 0.78$\pm$0.0028\tabularnewline
\hline 
\end{tabular}
\end{table}

%********************************************************************************
\section{Conclusions and Future Work}
\label{sec:conclusionsAndFutureWork}

%********************************************************************************
\section*{Acknowledgements}

%********************************************************************************
\bibliographystyle{plain}
\bibliography{refs}

%----------------------------------------------------------------------

\end{document}
%%% Local Variables:
%%% ispell-local-dictionary: "english"
%%% End:

### 2016-09-25 paper.tex
Fixed name of a figure
opened a section for methdology
Added description of setting up the experiments

@@
 \section{Introduction}
+
+\section{Methodology}
 
@@
 \begin{center}
-\includegraphics[scale=0.50]{confusion-matrix}
+\includegraphics[scale=0.50]{Confusion-matrix}
 \end{center}
@@
 Then I wrote another Python script to process these predicitons and calculate the precision and recall measurements as listed in this table.
+
+In all experiments, 10-folds cross validation methodology is applied for training and testing the developed classifiers.
+Moreover, in order to generate statistically reliable results, the 10-fold cross validation is repeated 10 times with different partitioning seeds then the average and standard deviation are calculated for each evaluation metric.
+
+In the first stage of the experiments the basic classifiers k-NN, NB, MLP, J48 and SVM are applied for predicting the sales level.
+The performance of some classifiers is highly affected by the initial values of their parameters.
+For this reason, initial experiment were conducted to tune the parameters of k-NN, SVM and MLP.
+For k-NN the best classification results were obtained with k=1.
+For SVM, a rough grid search was used, the value for the cost $C$ is set to 50 and $\gamma$  to 0.01.
+For MLP, the number of hidden neurons is set to (number of features+ number of output classes)/2.
 

### 2016-10-04 paper.tex
Some techniques described
And several parts of the paper modified. ;D

@@
-\documentclass{llncs}
+\documentclass[a4paper,10pt,onecolumn,preprint,3p]{elsarticle}
+
 \usepackage{graphics}
@@
 
-%%%%%%%%%%%%%%%% Titulo %%%%%%%%%%%%%%%
-\title{Predicting Levels of Sales for Newly Published Books using Cost-Sensitive Ensemble Methods}
-
-%%%%%%%%%%%%%%%% autores %%%%%%%%%%%%%%
-\author {}
-\institute{}
-% Antonio - Hossam add your 'official' e-mail here. ;)
-
-\date{}
+\journal{Journal of XXX}
 
 \begin{document}
+
+%\begin{frontmatter}
+
+%%%%%%%%%%%%%%%% Title %%%%%%%%%%%%%%%
+\title{Predicting Levels of Sales for Newly Published Books \\
+using Cost-Sensitive Ensemble Methods}
+
+%%%%%%%%%%%%%%%% Authors %%%%%%%%%%%%%%
+\author[abd]{Hossam Faris}
+\ead{hossam.faris@ju.edu.jo}
+\author[ugrtstc]{Antonio M. Mora}
+\ead{amorag@geneura.ugr.es}
+\author[ugratc]{Pedro A. Castillo}
+\ead{pacv@ugr.es}
+\author[ugratc]{J.J. Merelo}
+\ead{jmerelo@geneura.ugr.es}
+%\author[ugratc]{Pablo Garc\'{\i}a-S\'anchez}
+%\ead{pablogarcia@ugr.es}
+
+\address[abd]{Business Information Technology Department, King Abdullah II School for Information Technology \\
+The University of Jordan, Amman, Jordan}
+\address[ugrtstc]{Department of Signal Theory, Telematics and Communications, ETSIIT and CITIC \\
+University of Granada, Granada, Spain}
+\address[ugratc]{Department of Computer Architecture and Computer Technology, ETSIIT and CITIC \\
+University of Granada, Granada, Spain}
+
 \maketitle
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{abstract}
@@
 
-%********************************************************************************
+\begin{keyword}
+% Antonio - to refine later
+Book sales forecasting \sep Decision-aid models \sep Feature selection \sep Classification  
+\end{keyword}
 
+%\end{frontmatter}
+
+%*******************************************************************************
+%										INTRODUCTION
+%*******************************************************************************
 \section{Introduction}
+\label{sec:intro}
 
+%*******************************************************************************
+%										METHODOLOGY
+%*******************************************************************************
 \section{Methodology}
+\label{sec:methodology}
 
+%*******************************************************************************
+%										MATERIALS AND METHOD
+%*******************************************************************************
 \section{Materials and methods}
+\label{sec:materials}
+
+%-------------------------- BASIC CLASSIFIERS --------------------------
 \subsection{Basic classifiers}
+\label{subsec:classifiers}
 
@@
 \item \textbf{$k$-Nearest Neighbors ($k$-NN)}
+The kNN \cite{Aha1991,Mitchell1997} method is an instance-based classifier in 
+which unknown patterns/instances are classified by relating them to the labelled ones, using a distance measure or function, usually Euclidean or Minkowsky distances.
 
-\item \textbf{Naive Bayes classifier}
+The algorithm is based on the idea that two patterns with a high distance between them are less likely to belong to the same class than two close ones.
 
-\item \textbf{C4.5 Decision Trees}
+In the simplest approach, for every unknown instance to classify, the algorithm finds its nearest neighbour (in the patterns space), and assigns the class of that neighbour to the unknown pattern.
+However, it is more common to apply a more robust approach, in which $k$ neighbours are located, and thus, assigning the majority class of these instances to the unclassified pattern.
 
-\item \textbf{Multilayer Perceptron neural networks (MLP)}
+\item \textbf{Naive Bayes classifier (NB)}
+
+This is a type of probabilistic classifier, based on the Bayes' Theorem \cite{AI-book_Bayes}, which considers a \textit{naive} (or strong) independence between the variables of the samples to be classified.
+
+It is normally used as a baseline for comparison, because it usually yields competitive results in low computational time.
+Moreover, naive Bayes classifier shows a very good performance when there is considered a supervised training stage.
+
+This method has a very good scalability, requiring a linear number of parameters to work, depending on the number of variables of the problem.
+These parameters are the mean and standard deviations of the variables of every class.
+Thus, it just evaluates closed-form expressions, not needing to iterate to refine the solutions as most of methods do.
+
+\item \textbf{J48 - Decision Trees (DT)}
+
+This method is an implementation of the C4.5 classifier, which generates the so-called \textit{decision trees}.
+It was introduced in 1993 by Quinlan \cite{Quinlan1993} as an extension of the ID3 algorithm \cite{Mitchell1997}.
+
+The algorithm builds a decision tree using the attributes of the input patterns as nodes and considering its values for defining a decision in that node.
+Thus, for each node, the best attribute for splitting the training set is selected.
+The criteria for choosing one attribute is based on the difference of entropy (normalized information gain) obtained by every possible division.
+The one which yields the highest information gain is chosen as the best.
+This process is repeated for the subsequent data subsets, building subtrees.
+Normally, the decision tree is iteratively refined (or pruned) to maximize these gains and to avoid useless subtrees.
+
+\item \textbf{Multilayer Perceptron Neural Network (MLP)}
+
+It is an artificial neural network generally used for classification or 
+approximation/regression problems \cite{Rosenblatt1962,Widrow1990}.
+It maps the input data onto an appropriate output, as a generalisation of the standard linear perceptron that uses several layers of nodes, called neurons.
+Each neuron consists of a linear combination of weighted inputs which is passed through a non-linear activation function to produce its output.
+
+Thus, a MLP is able to solve linearly inseparable problems \cite{SteinwenderBitzer2003}. It is normally trained using a supervised learning 
+technique called \textit{back-propagation}.
+This method was proposed by Werbos, Parker and Rumelhart et al.
+\cite{Werbos1974,Parker1985,Rumelhart1985}, and consists in updating the weights of the output layer neurons according to the obtained erroneous output.
+Then, the weights are updated inversely up to the input layer.
+There are normally two hidden layers, as some works \cite{Lippmann1987,Bishop1996} demonstrated to be enough to 
+create classifying regions of any kind.
 
 \item \textbf{Support Vector Machines (SVM)}
+SVM \cite{Cortes1995,Shevade2000} is a method which applies statistical learning theory.
+In classification problems, the algorithm searches for an optimal hyperplane that separates two classes, maximising the margin between them.
+This hyperplane is defined by a subset of training set samples, called support vectors.
+
+This method is highly robust and reliable even if the space is highly dimensional and the problem is not linearly separable.
+
+SVM has been successfully applied in forecasting and classification problems \cite{Cao2003,MinSVM05,Jari2008}.
 
@@
 
+%-------------------------- ENSEMBLE CLASSIFIERS --------------------------
 \subsection{Ensemble classifiers}
+\label{subsec:ensembles}
 
@@
 \item \textbf{Random Forest}
+This method is based on the construction of a set of decision trees using a stochastic process over the basis of C4.5 algorithm. It was proposed by Breiman
+\cite{Breiman2001} and aims to create independent and uncorrelated trees based on different and random input vectors, following the same distribution. 
+The result is the average of the generated trees during the process.
 \end{itemize}
 
+%*******************************************************************************
+%										COST SENSITIVE CLASSIFICATION
+%*******************************************************************************
 \section{Cost sensitive classification}
+\label{sec:cost_sensitive_classification}
 
+%------------------------ COST SENSITIVE LEARNING ------------------------
 \subsection{Cost sensitive learning}
+\label{subsec:cost_learning}
+
+%------------------------ COST SENSITIVE CLASSIFICATION ------------------------
 \subsection{Cost sensitive classification}
+\label{subsec:cost_classification}
 
+%*******************************************************************************
+%										DATASET
+%*******************************************************************************
 \section{Dataset description}
+\label{sec:dataset}
 
 The obtained dataset contains collected information about 6083 different books produced by 209 publishers.
-Each book in the dataset is represented by 10 feature as shown in Table \ref{tabla:params_pre_sales}.
+Each book or pattern in the dataset is represented by 10 features as shown in Table \ref{tabla:params_pre_sales}.
 
-\begin{table}
+\begin{table*}
 \caption{Pre-sales features and Sales level(Output class). } 
@@
 \end{center}
-\end{table}
+\end{table*}
 
@@
 
+%*******************************************************************************
+%										EVALUATION MEASUREMENTS
+%*******************************************************************************
 \section{Evaluation measurements}
+\label{sec:eval_measures}
 
 To evaluate the developed classification models, first, we refer the confusion matrix shown in Table \ref{fig:confusionmatrix} which is considered as a basic source for evaluating any binary classification model.
-In our case which is a multiclass prediction problem, this matrix can be expanded with a row and column for each class to evaluate the multiclass classfication models.
+In our case which is a multiclass prediction problem, this matrix can be expanded with a row and column for each class to evaluate the multiclass classification models.
 Three measurements are used to evaluate the applied classifiers: accuracy rate, precision and recall.
@@
 
+%*******************************************************************************
+%										EXPERIMENTS AND RESULTS
+%*******************************************************************************
 \section{Experiments and results}
+\label{sec:experiments_results}
 
@@
 
-%********************************************************************************
+%*******************************************************************************
+%										CONCLUSIONS AND FUTURE WORK
+%*******************************************************************************
 \section{Conclusions and Future Work}
-\label{sec:conclusionsAndFutureWork}
+\label{sec:conclusions_future_work}
 
@@
 
+This work has been supported in part by projects PreTEL (PRM Consultores - Trevenque S.L.), TIN2014-56494-C4-3-P and TEC2015-68752 (Spanish Ministry of Economy and Competitiveness and FEDER), PRY142/14 (Fundaci{\'o}n P{\'u}blica Andaluza Centro de Estudios Andaluces en la IX Convocatoria de Proyectos de Investigaci{\'o}n), and PROY-PP2015-06 (Plan Propio 2015, funded by the University of Granada, Spain).
+
 %********************************************************************************
-\bibliographystyle{plain}
+\bibliographystyle{elsarticle-num}
 \bibliography{refs}
@@
 \end{document}
-%%% Local Variables:
-%%% ispell-local-dictionary: "english"
-%%% End:

### 2016-10-08 paper.tex
Added ensemble classifiers figures
Added results of ensemble classifiers

@@
 
-\usepackage{graphics}
+\usepackage{graphics,subfigure}
 \usepackage{amssymb}
@@
 \label{sec:methodology}
+
+\begin{figure*}[ht]
+\begin{center}
+\includegraphics[scale=0.40]{books_methodology}
+\end{center}
+\caption{Proposed methodology.}
+\label{fig:count}
+\end{figure*}
 
@@
 
+The developed classifiers are assessed by measuring their accuracy and the precision and recall of each class label.
+Evaluation measures for all classifiers are shown in Table \ref{table:basic_classifiers}.
+It can be noticed that all classifiers have obtained very close accuracy ratios with a slight advantage for the MLP network with 71\% accuracy.
+In general, accuracy rates don't give an insight on how the classifier performes regarding each class.
+Therefore, precision and recall rates are examined.
+\\
+
 \begin{table}
@@
 \end{tabular}
+\label{table:basic_classifiers}
+\end{table}
+
+\begin{figure*}[ht]
+
+\centerline{\includegraphics[scale=0.42]{RF}}
+
+\caption{Performance of RF classifier over different number of trees.}
+\label{fig:count}
+\end{figure*}
+
+\begin{figure*}[ht]
+\centerline{
+\includegraphics[scale=0.46]{Bagging}}
+
+\caption{Performance of Bagging classifier over different number of iterations.}
+\label{fig:count}
+\end{figure*}
+
+\begin{figure*}[ht]
+\centerline{
+\includegraphics[scale=0.46]{Adaboost}
+}
+\caption{Performance of Adaboost classifier over different number of iterations.}
+\label{fig:count}
+\end{figure*}
+
+\begin{table}
+\caption{Classification results using ensemble classifiers (RF, AdaBoost and Bagging)}
+\centering{}%
+\begin{tabular}{|c|c|c|c|}
+\hline 
+ & RF  &  AdaBoost &  Bagging \tabularnewline
+\hline 
+ \hline $Accuracy$ & 0.741 $\pm$ 0.002 & 0.743 $\pm$ 0.0023 & 0.735 $\pm$ 0.0022 \tabularnewline 
+ \hline 
+ \hline $Recall_{L}$ & 0.796 $\pm$ 0.0038 & 0.793 $\pm$ 0.0038 & 0.792 $\pm$ 0.0048 \tabularnewline 
+ \hline $Precision_{L}$ & 0.823 $\pm$ 0.0035 & 0.827 $\pm$ 0.0032 & 0.814 $\pm$ 0.0043 \tabularnewline 
+ \hline 
+ \hline $Recall_{M}$ & 0.748 $\pm$ 0.0033 & 0.75 $\pm$ 0.0029 & 0.738 $\pm$ 0.0038 \tabularnewline 
+ \hline $Precision_{M}$ & 0.712 $\pm$ 0.0026 & 0.716 $\pm$ 0.0032 & 0.707 $\pm$ 0.004 \tabularnewline 
+ \hline 
+ \hline $Recall_{H}$ & 0.68 $\pm$ 0.0073 & 0.684 $\pm$ 0.0051 & 0.667 $\pm$ 0.0065 \tabularnewline 
+ \hline $Precision_{H}$ & 0.666 $\pm$ 0.0037 & 0.667 $\pm$ 0.0029 & 0.663 $\pm$ 0.004 \tabularnewline 
+ \hline 
+ \hline $Recall_{VH}$ & 0.723 $\pm$ 0.0054 & 0.727 $\pm$ 0.0041 & 0.731 $\pm$ 0.0057 \tabularnewline 
+ \hline $Precision_{VH}$ & 0.816 $\pm$ 0.0051 & 0.808 $\pm$ 0.0056 & 0.793 $\pm$ 0.0069 \tabularnewline 
+\hline 
+\end{tabular}
+\label{table:basic_classifiers}
 \end{table}

### 2016-10-17 paper.tex
fixing figure labels
fixing table labels
Some comments

@@
 \caption{Proposed methodology.}
-\label{fig:count}
+\label{fig:methodology}
 \end{figure*}
+% Antonio - I like this figure, however, it seems on it that the results of the basic classifier are used as 'starting point' of the ensembles, and the results of these methods are used in the cost sensitive classification...
+is this correct?
+Otherwise, maybe we should change the design of the figure.
+;D
 
@@
 
-Table \ref{table:freq} and Figure \ref{fig:count} reveal more information about the nature of the dataset.
-We can notice that most of 77\% of the boos investigated are categorized as VL and L with limited number of sales.
+Table \ref{table:freq} and Figure \ref{fig:count} 
+% Antonio - Not sure which Figure did you refer to... Maybe should they be Tables 'params_pre-sales' and 'freq'? :D
+reveal more information about the nature of the dataset.
+We can notice that most of 77\% of the books investigated are categorized as VL and L with limited number of sales.
 On the other side, the books that achieved more than 2000 sold copies are just around 4\%.
@@
 Precision is the ratio of the correctly classified instances as $i$ to the number of instances classified as $i$.
-On the other side, recall is the ratio of the correctly classified instances as $i$ to the number of actual $i$ instances .
+On the other side, recall is the ratio of the correctly classified instances as $i$ to the number of actual $i$ instances.
 Precision and recall are given in Equation \ref{equation:precision} and \ref{equation:recall}, respectively.
@@
 \caption{Default cost matrix.}
-\label{fig:count}
+\label{fig:Default_cost_matrix}
 \end{figure*}
@@
 It can be noticed that all classifiers have obtained very close accuracy ratios with a slight advantage for the MLP network with 71\% accuracy.
-In general, accuracy rates don't give an insight on how the classifier performes regarding each class.
+In general, accuracy rates don't give an insight on how the classifier performs regarding each class.
 Therefore, precision and recall rates are examined.
@@
 
-\centerline{\includegraphics[scale=0.42]{RF}}
+\centerline{\includegraphics[scale=0.46]{RF}}
 
 \caption{Performance of RF classifier over different number of trees.}
-\label{fig:count}
+\label{fig:PerformanceRF}
 \end{figure*}
@@
 \caption{Performance of Bagging classifier over different number of iterations.}
-\label{fig:count}
+\label{fig:PerformanceBagging}
 \end{figure*}
@@
 \caption{Performance of Adaboost classifier over different number of iterations.}
-\label{fig:count}
+\label{fig:PerformanceAdaboost}
 \end{figure*}
+
+% Antonio - Just a comment about colors of the graphs. If one prints them in grey scale it cannot be distinguished for instance H and VH lines. ;)
 
@@
 \end{tabular}
-\label{table:basic_classifiers}
+\label{table:ensemble_classifiers}
 \end{table}
@@
 
-This work has been supported in part by projects PreTEL (PRM Consultores - Trevenque S.L.), TIN2014-56494-C4-3-P and TEC2015-68752 (Spanish Ministry of Economy and Competitiveness and FEDER), PRY142/14 (Fundaci{\'o}n P{\'u}blica Andaluza Centro de Estudios Andaluces en la IX Convocatoria de Proyectos de Investigaci{\'o}n), and PROY-PP2015-06 (Plan Propio 2015, funded by the University of Granada, Spain).
+This work has been supported in part by projects PreTEL (PRM Consultores - Trevenque S.L.), TIN2014-56494-C4-3-P and TEC2015-68752 (Spanish Ministry of Economy and Competitiveness and FEDER), and PROY-PP2015-06 (Plan Propio 2015, funded by the University of Granada, Spain).
 

### 2016-10-17 paper.tex
A couple of comments more

@@
 Table \ref{table:freq} shows the ranges of total sales that correspond to each category along with the number of sold books that fall in.
+% Antonio - We must explain how did we obtain or 'define' these categories... an expert's opinion or so. ;D
 
 Table \ref{table:freq} and Figure \ref{fig:count} 
-% Antonio - Not sure which Figure did you refer to... Maybe should they be Tables 'params_pre-sales' and 'freq'? :D
-reveal more information about the nature of the dataset.
-We can notice that most of 77\% of the books investigated are categorized as VL and L with limited number of sales.
-On the other side, the books that achieved more than 2000 sold copies are just around 4\%.
-This makes the problem of identifying those two categories much harder.
+% Antonio - Not sure which Figure did you refer to... Maybe should they be Tables 'params_pre-sales' and 'freq'?
+reveal more information about the nature of the dataset. We can notice that most of 77\% of the books investigated are categorized as VL 
+% Antonio - there is not a VL category, is there? I guess you mean Low and Medium, right?
+and L with limited number of sales. On the other hand, the books that achieved more than 2000 sold copies are just around 4\%. This makes the problem of identifying those two categories much harder.
+
+% Antonio - I think we must explain better about the new categorical feature and the use of GP (why GP, its advantages, and so on).
+I mean, the following sentence was a bit disconnected from the previous.
+;)
 The new categorical feature is used to replace the old numerical Total Sales feature in the GP classification case.

### 2016-11-13 paper.tex
modified dataset description

--- 2016-10-17 paper.tex
@@
 ;D
+% Hossam: I have changed the figure as Antonio suggested ;)
 
@@
 Table \ref{table:freq} shows the ranges of total sales that correspond to each category along with the number of sold books that fall in.
+% Antonio - We must explain how did we obtain or 'define' these categories... an expert's opinion or so. ;D
 
-Table \ref{table:freq} and Figure \ref{fig:count} 
-% Antonio - Not sure which Figure did you refer to... Maybe should they be Tables 'params_pre-sales' and 'freq'? :D
-reveal more information about the nature of the dataset.
-We can notice that most of 77\% of the books investigated are categorized as VL and L with limited number of sales.
-On the other side, the books that achieved more than 2000 sold copies are just around 4\%.
-This makes the problem of identifying those two categories much harder.
-The new categorical feature is used to replace the old numerical Total Sales feature in the GP classification case.
+Table \ref{table:freq} reveal more information about the nature of the dataset.
+We can notice that most of the investigated books are categorized as Low and Medium levels forming 26.8\% and 36.4\% of the dataset, respectively.
+High volumes of sold books that range from 300 up to 1000 are categorized as High volume of sales and form 24\% of the dataset.
+On the other hand, books that achieved more than 1000 sold copies are categorized as Very High and they form around 12.8\% of the dataset.
+Our focus in this study is to identify the more profitable categories which are High and Very High.
+However, since the latter category is much smaller than the other ones, we can describe our dataset as imbalanced dataset which makes the problem of identifying this category harder and more challenging.
 
@@
 % Antonio - Just a comment about colors of the graphs. If one prints them in grey scale it cannot be distinguished for instance H and VH lines. ;)
+% Hossam- I have updated all figure as you Antonio suggested and I have added also Low and Medium results to the figures.
 

### 2016-12-02 paper.tex
extended description
about discretization
Added Bagging subsection

@@
 \begin{itemize}
-\item \textbf{Bagging}
+\item \textbf{Bagging} Bagging which is called also Bootstrap aggregating is an ensemble meta-algorithm introduced by \citet{B1996}.
+Bagging works by training base classifiers (usually decision tree classifiers) based on generated new datasets from the original training dataset.
+The new generated datasets are drawn randomly with replacement in a size almost equal to the original dataset.
+The final classifier's output is based on aggregating the classifiers by taking a majority or weighted vote.
+
 \item \textbf{Boosting}
 \item \textbf{Random Forest}
-This method is based on the construction of a set of decision trees using a stochastic process over the basis of C4.5 algorithm. It was proposed by Breiman
-\cite{Breiman2001} and aims to create independent and uncorrelated trees based on different and random input vectors, following the same distribution. 
+This method is based on the construction of a set of decision trees using a stochastic process over the basis of C4.5 algorithm.
+It was proposed by Breiman in \cite{Breiman2001} and aims to create independent and uncorrelated trees based on different and random input vectors, following the same distribution.
 The result is the average of the generated trees during the process.
@@
 Table \ref{table:freq} shows the ranges of total sales that correspond to each category along with the number of sold books that fall in.
+Discretization of the volume of sales was conducted with the aid of experts in the domain of editorial management business by defining the the four categories.
+
 % Antonio - We must explain how did we obtain or 'define' these categories... an expert's opinion or so. ;D
+% Hossam - I have added this to the latter paragraph. Please check.
 
@@
 In general, accuracy rates don't give an insight on how the classifier performs regarding each class.
-Therefore, precision and recall rates are examined.
+Therefore, precision and recall rates are examined for each class.
 \\

### 2016-12-02 paper.tex
Added Boosting subsection

@@
 \begin{itemize}
-\item \textbf{Bagging} Bagging which is called also Bootstrap aggregating is an ensemble meta-algorithm introduced by \citet{B1996}.
+\item \textbf{Bagging} 
+Bagging which is called also Bootstrap aggregating is an ensemble meta-algorithm introduced by \citet{B1996}.
 Bagging works by training base classifiers (usually decision tree classifiers) based on generated new datasets from the original training dataset.
@@
 \item \textbf{Boosting} 
+Boosting is an ensemble classification algorithm which was first proposed by \citet{schapire1990strength} in \citet{schapire1990strength}.
+Boosting is based on the idea that a set of weak classifiers can create a stronger one.
+In this work we adopt a powerful a variation of boosting called Adaptive Boosting or "Adaboost" for short \cite{FS1997}.
+Adaboost operates on a training dataset ${(x_{1},y_{1}),...,(x_{m},y_{m})}$ where each $x_{i}$ is a set of inputs belongs to some domain $X$ and each $y_{i}$ belongs to some label $Y$ assuming $Y$ is a binary class set $\{+1,-1\}$.
+
+During the learning process, Adaboost modifies the dataset by weighting its samples.
+These weights are updated every time a new classifier is trained to increase the focus on the difficult data instances.
+Consequently, the final generated classifier is a weighted combination of all trained base classifiers.
+According to many previous works, Adaboost is resistant to overfitting and it can outperform many other state-of-the-art classification techniques.
+
 \item \textbf{Random Forest}

### 2016-12-02 paper.tex
Comments on basic results

@@
 Therefore, precision and recall rates are examined for each class.
-\\
+Precision and recall values in Table \ref{table:basic_classifiers} show that J48 classifier achieved the highest recall value of 72\% for (VH) class with 74\% precision.
+The second best classifier for this important class is MLP with 68\% recall and 77\% precision.
+Having a look at the second important class which is (H), we can see that MLP has the highest recall with 65\% and a precision of 62\%.
+J48 comes second for the (H) class with a slight decrease in the recall value.
 

### 2016-12-03 paper.tex
Commenting second stage of experiments

@@
 
-\begin{figure*}[ht]
+In the next stage of the experiments, the ensemble classifiers (i.e.
+RF, Bagging and AdaBoost) are applied and evaluated.
+For Bagging and AdaBoost, the base classifier is selected to be the J48 decision tree algorithm.
+This selection is for three reasons: first, the J48 algorithm achieved very competitive evaluation results in the previous phase.
+Second, J48 is much faster as a learning algorithm compared to the MLP network which was the second candidate.
+Third, tree induction algorithms are good candidates as base classifiers in bagging and boosting because support diversity among the learners.
+It is well known that tree induction algorithms are relatively unstable (i.e.
+weak) base learners, meaning that small changes in the training data lead to big changes in the developed models.
+
+\begin{figure*}
 
@@
 
-\begin{figure*}[ht]
+\begin{figure*}
 \centerline{

### 2016-12-03 paper.tex
adding text to the abstract

@@
 \begin{abstract}
+
+An important task when publishing a new book is determining an adequate number 
+of copies to be printed, but not a excesive number, as the unsold volumes will 
+lead to losses.
+In this paper, we face the problem of predicting total sales using cost-sensitive
+ensemble methods, that can be used as decision-aid tools for publishers, which 
+can provide a reliable guidance on the decision process of publishing a book. 
+A real dataset including the complete sales data for books published in Spain 
+across several years has been used to create forecasting models.
+Results show that \emph{EXPLAIN THE RESULTS OBTAINED}.
 
@@
 Boosting is based on the idea that a set of weak classifiers can create a stronger one.
-In this work we adopt a powerful a variation of boosting called Adaptive Boosting or "Adaboost" for short \cite{FS1997}.
+In this work we adopt a powerful a variation of boosting called Adaptive Boosting or ''Adaboost'' for short \cite{FS1997}.
 Adaboost operates on a training dataset ${(x_{1},y_{1}),...,(x_{m},y_{m})}$ where each $x_{i}$ is a set of inputs belongs to some domain $X$ and each $y_{i}$ belongs to some label $Y$ assuming $Y$ is a binary class set $\{+1,-1\}$.

### 2016-12-04 paper.tex
fixing the format style (to show the abstract)
adding text to the INTRODUCTION

@@
-\documentclass[a4paper,10pt,onecolumn,preprint,3p]{elsarticle}
+\documentclass[a4paper,10pt,twocolumn,preprint,3p]{elsarticle}
 
@@
 
-\journal{Journal of XXX}
+\journal{Journal of XXXXXXXXX}
 
@@
 
-%\begin{frontmatter}
+\begin{frontmatter}
 
@@
 
-\maketitle
+%\maketitle
 
@@
 
-%\end{frontmatter}
+\end{frontmatter}
 
@@
 \label{sec:intro}
+
+Determining the number of copies of a new book should the publisher print, the 
+so called {\em print run}, for delivery to bookstores is a challenging problem.
+Thus, it is extremely important to develop an accurate predictive method which 
+could forecast the future sales a new book will achieve, in order to optimise 
+production schedules, improve the publishing company profits and minimise 
+losses \cite{Zhao2001}.
+
+Printing an adequate number of copies, but not too many, might reduce the number 
+of unsold volumes, which could lead to losses. 
+In another hand, if the number of printed copies is not enough, the publisher 
+company might have temporary losses due to a lack of supply.
+
+Moreover, according to results reported in \cite{Fildes2010,Saeed2008}, reducing 
+the error in estimated sales leads to the improvement of sales predictions and 
+thus, in an enhancement in the whole production process.
+
+\textbf{UNDER CONSTRUCTION ;) }
+
+To make the print run as close as possible to the actual level of sales, it is 
+essential to have an estimation of those sales.
+In this sense, this paper continues our previous work on book sales prediction 
+\cite{Castillo2016books} in which the main factors influencing sales where 
+analyzed in order to create a tool that the publisher can use to decide how many 
+books should be printed.
+
+In this paper, the challenge we are taking is determining the actual level of 
+sales a new book will achieve.
+
+The rest of this paper is structured as follows: 
+A detailled review of the approaches related to sales prediction in similar scopes is presented in Section \ref{sec:soa}.
+Then, Section \ref{sec:methodology} details the methodology considered in the present study. 
+Obtained results after extensive experimentation are presented in Section \ref{sec:experiments_results}.
+Finally, conclusions and future lines of work are presented in Section \ref{sec:conclusions_future_work}.
+
+%*******************************************************************************
+%										STATE OF THE ART
+%*******************************************************************************
+\section{State of the art on sales forecasting} 
+\label{sec:soa}
+
+\textbf{UNDER CONSTRUCTION ;) }
 

### 2016-12-04 paper.tex
fixing references

@@
 \begin{itemize}
-\item \textbf{Bagging} 
-Bagging which is called also Bootstrap aggregating is an ensemble meta-algorithm introduced by \citet{B1996}.
+\item \textbf{Bagging}: 
+Bagging which is called also Bootstrap aggregating is an ensemble meta-algorithm introduced in \cite{B1996}.
 Bagging works by training base classifiers (usually decision tree classifiers) based on generated new datasets from the original training dataset.
@@
 
-\item \textbf{Boosting} 
-Boosting is an ensemble classification algorithm which was first proposed by \citet{schapire1990strength} in \citet{schapire1990strength}.
+\item \textbf{Boosting}: 
+Boosting is an ensemble classification algorithm which was first proposed in \cite{schapire1990strength}.
 Boosting is based on the idea that a set of weak classifiers can create a stronger one.
@@
 
-\item \textbf{Random Forest}
+\item \textbf{Random Forest}:
 This method is based on the construction of a set of decision trees using a stochastic process over the basis of C4.5 algorithm.

### 2016-12-05 paper.tex
adding contents to INTRODUCTION

@@
 so called {\em print run}, for delivery to bookstores is a challenging problem.
-Thus, it is extremely important to develop an accurate predictive method which 
+
+Thus, it is extremely important to develop accurate predictive methods which 
 could forecast the future sales a new book will achieve, in order to optimise 
@@
 
+Usually the methods used to predict book sales have
+been generally based on experts' experience, who analyse data about sales and, 
+taking into account their knowledge of the industry, their experience, and their 
+perception about trends, could make decisions on the companies production.
+However, this process might be tedious, especially when the amount of data is 
+quite large. Moreover, different experts can reach different predictions from 
+the same dataset \cite{Sanders1994}.
+
 \textbf{UNDER CONSTRUCTION ;) }
@@
 books should be printed.
+In that paper, several regression methods were applied to estimate sales for new launched books using a real dataset of book sales related to the Spanish market, provided by the Spanish publishing company Trevenque Editorial S.L.\footnote{{\tt http://editorial.trevenque.es}
 
-In this paper, the challenge we are taking is determining the actual level of 
-sales a new book will achieve.
+However, as finding adequate forecasting techniques and selecting the best method 
+to use represent also a problem, we propose configuring complex models based on
+ensembles \cite{Qiu2014} in order to face the challenge of determining the actual 
+level of sales a new book will achieve.
+Moreover, since publishers need models to explain obtained predictions, and 
+`black box' forecasting methods may not be suitable, using these ensemble 
+models publishers will be able to combine their expert knowledge about the 
+market with the created forecasting models in order to get a reliable estimation 
+of book sales level.
 

### 2016-12-05 paper.tex
fixed footnote

@@
 books should be printed.
-In that paper, several regression methods were applied to estimate sales for new launched books using a real dataset of book sales related to the Spanish market, provided by the Spanish publishing company Trevenque Editorial S.L.\footnote{{\tt http://editorial.trevenque.es}
+In that paper, several regression methods were applied to estimate sales for new launched books using a real dataset of book sales related to the Spanish market, provided by the Spanish publishing company Trevenque Editorial S.L.\footnote{\tt http://editorial.trevenque.es}
 

### 2016-12-07 paper.tex
fixed tables
Abstract, Intro and comments revised
All around the paper. :D

@@
-\documentclass[a4paper,10pt,twocolumn,preprint,3p]{elsarticle}
+\documentclass[a4paper,10pt,onecolumn,preprint,3p]{elsarticle}
+% The format for draft in Elsevier is one column. ;D
 
@@
 
-An important task when publishing a new book is determining an adequate number 
-of copies to be printed, but not a excesive number, as the unsold volumes will 
-lead to losses.
-In this paper, we face the problem of predicting total sales using cost-sensitive
-ensemble methods, that can be used as decision-aid tools for publishers, which 
-can provide a reliable guidance on the decision process of publishing a book. 
-A real dataset including the complete sales data for books published in Spain 
-across several years has been used to create forecasting models.
+An important task when publishing a new book is determining an accurate number 
+of copies to be printed. Doing both an under- or an overestimation will lead to financial losses.
+In this paper, we address the problem of predicting total sales using cost-sensitive ensemble methods.
+% Antonio - explain briefly what are them
+These can be used as reliable decision-aid tools for publishers, as a part of the final stages of the editorial process. 
+Thus, a real dataset including the complete sales data for books published in Spain across several years has been used to compute the prediction models.
+% Antonio - extend a bit this with the followed methodology.
 Results show that \emph{EXPLAIN THE RESULTS OBTAINED}.
@@
 % Antonio - to refine later
-Book sales forecasting \sep Decision-aid models \sep Feature selection \sep Classification  
+Book sales forecasting \sep Decision-aid models \sep Feature selection \sep Classification \sep Ensemble methods
 \end{keyword}
@@
 
-Determining the number of copies of a new book should the publisher print, the 
-so called {\em print run}, for delivery to bookstores is a challenging problem.
+Inside the publishing process of a new book, deciding the best {\em print run}, i.e. the number of copies to be printed and delivered to bookstores, is a very challenging problem.
 
-Thus, it is extremely important to develop accurate predictive methods which 
-could forecast the future sales a new book will achieve, in order to optimise 
-production schedules, improve the publishing company profits and minimise 
-losses \cite{Zhao2001}.
+To this end, it is extremely important to develop accurate predictive models which could forecast the future sales a new book will achieve, in order to optimise production schedules: to improve the publishing company profits and to minimise losses \cite{Zhao2001}, due both to the excess or to the scarcity of units.
+%
+%Printing an adequate number of copies, but not too many, might reduce the number 
+%of unsold volumes, which could lead to losses. 
+%In another hand, if the number of printed copies is not enough, the publisher 
+%company might have temporary losses due to a lack of supply.
+%
+Since, according to the results reported in \cite{Fildes2010,Saeed2008}, reducing the error in estimated sales leads to an enhancement of the whole production process.
 
-Printing an adequate number of copies, but not too many, might reduce the number 
-of unsold volumes, which could lead to losses. 
-In another hand, if the number of printed copies is not enough, the publisher 
-company might have temporary losses due to a lack of supply.
+Usually the prediction of book sales has been generally based on experts' experience.
+They analyse data about sales and, taking into account their knowledge of the industry, the production process, and their perception about trends, and take decisions on the production and publication process.
+However, this process might be tedious, especially when the amount of data is 
+quite large. Moreover, the results are not robust, since different experts can reach different predictions from the same dataset \cite{Sanders1994}.
 
-Moreover, according to results reported in \cite{Fildes2010,Saeed2008}, reducing 
-the error in estimated sales leads to the improvement of sales predictions and 
-thus, in an enhancement in the whole production process.
-
-Usually the methods used to predict book sales have
-been generally based on experts' experience, who analyse data about sales and, 
-taking into account their knowledge of the industry, their experience, and their 
-perception about trends, could make decisions on the companies production.
-However, this process might be tedious, especially when the amount of data is 
-quite large. Moreover, different experts can reach different predictions from 
-the same dataset \cite{Sanders1994}.
-
-\textbf{UNDER CONSTRUCTION ;) }
+\textbf{UNDER CONSTRUCTION}
+% Antonio - I remove the ';)' because I want to check the parentheses correspondence and it breaks it. :P
 
@@
 
+% Antonio - We must remark that this approach is based in classification rather than regression, which is based on levels of sales (classes) instead of on numerical results.
+These will be easily 'explained' or justified for a (human) publisher.
+% Previous work also presented the results in an intelligible way, since it offered decision trees as the last output, but they include regression computation in the leaves.
+Here the models/outputs will be easily interpreted.
+
 The rest of this paper is structured as follows: 
-A detailled review of the approaches related to sales prediction in similar scopes is presented in Section \ref{sec:soa}.
+A detailed review of the approaches related to sales prediction in similar scopes is presented in Section \ref{sec:soa}.
 Then, Section \ref{sec:methodology} details the methodology considered in the present study. 
@@
 
-\textbf{UNDER CONSTRUCTION ;) }
+\textbf{UNDER CONSTRUCTION}
+% Antonio - I remove the ';)' because I want to check the parentheses correspondence and it breaks it. :P
 
@@
 % Hossam: I have changed the figure as Antonio suggested ;)
+% Antonio - It is better now, however, is the evaluation the last stage of the methodology?
+Won't we choose the best approach based on the results?
+Won't we compose an useful tool with it as in previous paper?
+I mean a decision tree or so.
+;D
 
@@
 \item \textbf{Bagging}: 
-Bagging which is called also Bootstrap aggregating is an ensemble meta-algorithm introduced in \cite{B1996}.
+It is also called \textit{Bootstrap aggregating} is an ensemble meta-algorithm introduced in \cite{B1996}.
 Bagging works by training base classifiers (usually decision tree classifiers) based on generated new datasets from the original training dataset.
 The new generated datasets are drawn randomly with replacement in a size almost equal to the original dataset.
-The final classifier's output is based on aggregating the classifiers by taking a majority or weighted vote.
+% Antonio - I cannot understand this sentence (upper one). :/
+The final classifier's output is based on aggregating the base classifiers by taking a majority or weighted vote.
 
 \item \textbf{Boosting}: 
-Boosting is an ensemble classification algorithm which was first proposed in \cite{schapire1990strength}.
-Boosting is based on the idea that a set of weak classifiers can create a stronger one.
-In this work we adopt a powerful a variation of boosting called Adaptive Boosting or ''Adaboost'' for short \cite{FS1997}.
-Adaboost operates on a training dataset ${(x_{1},y_{1}),...,(x_{m},y_{m})}$ where each $x_{i}$ is a set of inputs belongs to some domain $X$ and each $y_{i}$ belongs to some label $Y$ assuming $Y$ is a binary class set $\{+1,-1\}$.
+It is an ensemble classification algorithm which was firstly proposed in \cite{schapire1990strength}.
+Boosting is founded on the idea that a set of weak classifiers can create a stronger one.
+In this work we adopt a powerful a variation of boosting called \textit{Adaptive Boosting} or ``AdaBoost'' for short \cite{FS1997}.
+AdaBoost operates on a training dataset ${(x_{1},y_{1}),...,(x_{m},y_{m})}$ where each $x_{i}$ is a set of inputs belonging to some domain $X$ and each $y_{i}$ belongs to some label $Y$ assuming $Y$ is a binary class set $\{+1,-1\}$.
 
-During the learning process, Adaboost modifies the dataset by weighting its samples.
-These weights are updated every time a new classifier is trained to increase the focus on the difficult data instances.
-Consequently, the final generated classifier is a weighted combination of all trained base classifiers.
-According to many previous works, Adaboost is resistant to overfitting and it can outperform many other state-of-the-art classification techniques.
+During the learning process, AdaBoost modifies the dataset by weighting its samples. These weights are updated every time a new classifier is trained to increase the focus 
+% Antonio - what is the focus here?
+on the difficult data instances. Consequently, the final generated classifier is a weighted combination of all trained base classifiers. According to many previous works, 
+% Antonio - if you say this, you must add some references. ;P
+AdaBoost is not affected 
+% Antonio - 'is not affected by' -> 'avoids'?
+by overfitting and it can outperform many other state-of-the-art classification techniques.
 
@@
 The result is the average of the generated trees during the process.
+
+% Antonio - we should improve a bit this description to do it more complete. ;)
+
 \end{itemize}
@@
 
-The output variable which is the total sales is a categorical variable the represent the level of the quantity sold of a given book.
-Four categories are used to represent the total sales level: Low (L), Medium (M), High (H) and Very High (VH).
+The output variable which is related to the total amount of sales is a categorical variable which represent the level of the quantity sold for a given book.
+Thus, four categories have been considered to represent these levels: \textit{Low (L)}, \textit{Medium (M)}, \textit{High (H)}, and \textit{Very High (VH)}.
 Table \ref{table:freq} shows the ranges of total sales that correspond to each category along with the number of sold books that fall in.
-Discretization of the volume of sales was conducted with the aid of experts in the domain of editorial management business by defining the the four categories.
-
-% Antonio - We must explain how did we obtain or 'define' these categories... an expert's opinion or so. ;D
-% Hossam - I have added this to the latter paragraph. Please check.
+The discretization of the volume of sales was conducted by an expert in the domain of editorial management business, who defined the four categories.
 
@@
 Evaluation measures for all classifiers are shown in Table \ref{table:basic_classifiers}.
-It can be noticed that all classifiers have obtained very close accuracy ratios with a slight advantage for the MLP network with 71\% accuracy.
-In general, accuracy rates don't give an insight on how the classifier performs regarding each class.
-Therefore, precision and recall rates are examined for each class.
-Precision and recall values in Table \ref{table:basic_classifiers} show that J48 classifier achieved the highest recall value of 72\% for (VH) class with 74\% precision.
-The second best classifier for this important class is MLP with 68\% recall and 77\% precision.
-Having a look at the second important class which is (H), we can see that MLP has the highest recall with 65\% and a precision of 62\%.
-J48 comes second for the (H) class with a slight decrease in the recall value.
 
-\begin{table}
+\begin{table*}
 \caption{Classification results using basic classifiers (without print-run)}
@@
 \label{table:basic_classifiers}
-\end{table}
+\end{table*}
+
+It can be noticed that all classifiers have obtained very close accuracy ratios with a slight advantage for the MLP network with 71\% accuracy.
+In general, accuracy rates don't give an insight on how the classifier performs regarding each class.
+Therefore, precision and recall rates are examined for each class.
+Precision and recall values in Table \ref{table:basic_classifiers} show that J48 classifier achieved the highest recall value of 72\% for (VH) class with 74\% precision.
+The second best classifier for this important class is MLP with 68\% recall and 77\% precision.
+Having a look at the second important class which is (H), we can see that MLP has the highest recall with 65\% and a precision of 62\%.
+J48 comes second for the (H) class with a slight decrease in the recall value.
 
@@
 
-% Antonio - Just a comment about colors of the graphs. If one prints them in grey scale it cannot be distinguished for instance H and VH lines. ;)
-% Hossam- I have updated all figure as you Antonio suggested and I have added also Low and Medium results to the figures.
-
-\begin{table}
+\begin{table*}
 \caption{Classification results using ensemble classifiers (RF, AdaBoost and Bagging)}
@@
 \label{table:ensemble_classifiers}
-\end{table}
+\end{table*}
 

### 2016-12-07 paper.tex
Modifications and comments here and there

@@
 %%%%%%%%%%%%%%%% Title %%%%%%%%%%%%%%%
-\title{Predicting Levels of Sales for Newly Published Books \\
+\title{Predicting Sales Level for Newly Published Books \\
 using Cost-Sensitive Ensemble Methods}
@@
 \ead{jmerelo@geneura.ugr.es}
-%\author[ugratc]{Pablo Garc\'{\i}a-S\'anchez}
-%\ead{pablogarcia@ugr.es}
 
@@
 \begin{abstract}
-
+%First you have to explain why it is enough to predict the level of
+%sales, and not the precise number. 
 An important task when publishing a new book is determining an accurate number 
@@
 % Antonio - extend a bit this with the followed methodology.
-Results show that \emph{EXPLAIN THE RESULTS OBTAINED}.
+% Explain also the method you are using and why it's an improvement
+% over the previous one - JJ
+Results show that %\emph{EXPLAIN THE RESULTS OBTAINED}.
 
@@
 
-Inside the publishing process of a new book, deciding the best {\em print run}, i.e. the number of copies to be printed and delivered to bookstores, is a very challenging problem.
+% You have to
+% 1. Explain the problem: predicting the sales level. 
+% 2. Briefly state what has been done so far (previous paper) and how
+% this improves over that paper. You will have to compare results,
+% too.
+% 3. Talk about the methodology and why we think this should give us
+% better results.
+% 4. Hint at how we are going to prove it.
 
-To this end, it is extremely important to develop accurate predictive models which could forecast the future sales a new book will achieve, in order to optimise production schedules: to improve the publishing company profits and to minimise losses \cite{Zhao2001}, due both to the excess or to the scarcity of units.
-%
-%Printing an adequate number of copies, but not too many, might reduce the number 
-%of unsold volumes, which could lead to losses. 
-%In another hand, if the number of printed copies is not enough, the publisher 
-%company might have temporary losses due to a lack of supply.
-%
+Inside the publishing process of a new book, deciding the optimal {\em
+  print run}, i.e. the number of copies to be printed and delivered to
+bookstores, is a very challenging problem, that is why it is extremely
+important to develop accurate predictive models which could forecast
+the future sales a new book will achieve, in order to optimise
+production schedules: to improve the publishing company profits and to
+minimise losses \cite{Zhao2001}, due both to the excess or to the
+scarcity of units. 
+%I would eliminate this paragraph. We have it on the other one.
 Since, according to the results reported in \cite{Fildes2010,Saeed2008}, reducing the error in estimated sales leads to an enhancement of the whole production process.
@@
 
-\textbf{UNDER CONSTRUCTION}
-% Antonio - I remove the ';)' because I want to check the parentheses correspondence and it breaks it. :P
-
+%\textbf{UNDER CONSTRUCTION}
+% Antonio - I remove the ';)' because I want to check the parentheses
+% correspondence and it breaks it. :P
+% Use comments for non-text comments. Like under construction - JJ
+% Define level of sales before you use it here. Is it the actual
+% number? A ballpark? If it's the actual number, it should be unit
+% sales - JJ 
 To make the print run as close as possible to the actual level of sales, it is 
@@
 
-However, as finding adequate forecasting techniques and selecting the best method 
-to use represent also a problem, we propose configuring complex models based on
-ensembles \cite{Qiu2014} in order to face the challenge of determining the actual 
+However, since finding adequate forecasting techniques and selecting the best method 
+to use represents also a problem, we propose configuring complex models based on
+ensembles \cite{Qiu2014} in order to determine the actual 
 level of sales a new book will achieve.
@@
 
-\textbf{UNDER CONSTRUCTION}
+%\textbf{UNDER CONSTRUCTION}
 % Antonio - I remove the ';)' because I want to check the parentheses correspondence and it breaks it. :P
@@
 \label{subsec:ensembles}
+
+% You should say something before and after this. Why ensemble would
+% work better, for instance - JJ
 
@@
 
-This work has been supported in part by projects PreTEL (PRM Consultores - Trevenque S.L.), TIN2014-56494-C4-3-P and TEC2015-68752 (Spanish Ministry of Economy and Competitiveness and FEDER), and PROY-PP2015-06 (Plan Propio 2015, funded by the University of Granada, Spain).
+This work has been supported in part by projects PreTEL (PRM
+Consultores - Trevenque S.L.), TIN2014-56494-C4-3-P and TEC2015-68752
+(Spanish Ministry of Economy and Competitiveness and FEDER), and
+PROY-PP2015-06 (Plan Propio 2015, funded by the University of Granada,
+Spain).
+% Is still this last grant running?
 

### 2016-12-08 paper.tex
adding new references (related to ensembles) and some sentences
working in the SoA

@@
 % over the previous one - JJ
+We evaluate our approach on the real data collected by a Spanish publishing company.
 Results show that %\emph{EXPLAIN THE RESULTS OBTAINED}.
@@
 
-Inside the publishing process of a new book, deciding the optimal {\em
+Reliable sales prediction can enhance the whole production process for different companies involved in manufacturing, marketing and trading.
+
+Specifically, focusing in the publishing process of a new book, deciding the optimal {\em
   print run}, i.e. the number of copies to be printed and delivered to
@@
 
+Sales prediction is an important problem that can improve the quality of business 
+strategy for different companies. 
+Traditionally, sales prediction problems have been solved using advaced methods 
+such as regression models \cite{Papalexopoulos1990}, neural networks \cite{Yoo1999}, 
+fuzzy systems \cite{Mastorocostas2001}, or mixture of methods \cite{Chang2006715,Meulstee2008,ChiJie2012}.
+
 %\textbf{UNDER CONSTRUCTION}
-% Antonio - I remove the ';)' because I want to check the parentheses correspondence and it breaks it. :P
 

### 2016-12-08 paper.tex
improving the SoA

@@
 
-%\textbf{UNDER CONSTRUCTION}
+The most used technique to tackle sales forecasting problems is time-series prediction methods
+\cite{Chu2003,Brown1959,Winters1960,Box1969,Papalexopoulos1990,KayacanUK10},
+however the correctness of the problem data strongly affects the predictions obtained.
+Moreover, this kind of methods are based on using historical data to make time series.
+However, in the case of new products sales prediction (such as the issue of new books), 
+there is no available historical sales data \cite{ChingChin2010}, 
+and only pre-sales data are available \cite{FaderHardie2005,Madsen2008}, 
+i.e. variables known before the product is on sale.
+
+Not only the lack of historical data makes this a complex problem, but also the fact 
+that several variables (seasonality, promotions, or fashions) might influence predictions
+\cite{Lapide1999,Thomassey2012,Xia2012,SThomassey2014,ChernWSF15}.
+
+Due to the difficulty this problem represents when forecasting sales of new 
+products, some authors have proposed using different data mining methods, such as
+data clustering and fuzzy neural networks \cite{Chang2009}  or
+extreme learning machine with adaptive metrics of inputs \cite{Xia2012}.
+In this sense, several authors have proposed using ensemble of models for sales forecasting, 
+as in \cite{ChiJie2012}, where a hybrid forecasting model integrates ensemble 
+empirical model decomposition and extreme learning machine to develop an effective 
+forecasting model for computer products sales.
+Also, Meulstee et al. \cite{Meulstee2008} developed an ensemble learning approach 
+for better handling of seasonal changes and fluctuations in consumer demands,
+while Chang et al. \cite{Chang2006715} integrated a fuzzy logic controller 
+and artificial neural network for sales forecasting in printed circuit board industry.
+Another authors have faced the problem of sales forecasting in textile-apparel 
+fashion industry (a very similar issue to the new book publishing problem) 
+using a clustering method together with decision trees, as in \cite{SThomassey2014},  or
+a forecasting method based on extreme machine learning with adaptive metrics of inputs \cite{Xia2012}.
+
+% TODO
 

### 2016-12-08 paper.tex
completing the SoA

@@
 
-Reliable sales prediction can enhance the whole production process for different companies involved in manufacturing, marketing and trading.
+Reliable sales prediction can enhance the whole production process for different 
+companies involved in manufacturing, marketing and trading.
+Moreover, in some real-world cases, such as consumer electronics, fashion products and books,
+new products are presented/launched every season; thus, accurate sales forecasting 
+models could help in marketing campaigns.
 
@@
 using a clustering method together with decision trees, as in \cite{SThomassey2014},  or
-a forecasting method based on extreme machine learning with adaptive metrics of inputs \cite{Xia2012}.
+a forecasting method based on extreme machine learning with adaptive metrics 
+of inputs \cite{Xia2012}.
+Ching et al. \cite{ChingChin2010} use a decision-support system to classify new 
+products (tea, cosmetics and soft drink) based on their sales patterns, assuming 
+that products in the same class would follow a similar sales pattern. 
+In any case, the proposed system can not deal with qualitative 
+data related to the products.
 
-% TODO
+Finally, in those problems where historical data are available, authors have 
+proposed applying classical time series forecasting methods.
+In \cite{Chang2009} a hybrid model integrating K-Means and fuzzy neural networks 
+to forecast the future sales of a printed circuit board is proposed.
+Recent works propose take advantage of information extracted from online reviews, 
+such as in \cite{ChernWSF15} where an analysis on historical data throughout online 
+reviews, reviewer characteristics, and review influences to understand how 
+electronic `word-of-mouth' influences product sales is presented.
+Similar works propose take advantage of information published on specialized 
+blogs \cite{Moon2010ICSSSM,Moon2010ICEC}, having confirmed relationships between 
+the number of blog references and book sales, at the time that different sales 
+patterns have been observed by analysing books in series (the first book published 
+takes the longest period to achieve every single sales scale, while the second book 
+takes the second longest period, and so on).
+In these cases, sales forecasting problems can be carried out thanks to a big 
+amount of online reviews and historical data.
+
+This paper continues our work on the prediction of sales of a new product for 
+which no historical data are available, and where the classical forecasting methods 
+based on time-series are not adequate.
+In this sense, in \cite{Castillo2016books} the main factors influencing sales where 
+analyzed in order to create a tool, based on several regression methods, that the 
+publisher can use to decide how many books should be printed.
+
+In this paper we address the problem of new book sales prediction using cost-sensitive ensemble methods.
+% TODO: complete this paragraph.
 

### 2016-12-09 paper.tex
Added intro to Ensembles section

@@
 
-% You should say something before and after this. Why ensemble would
-% work better, for instance - JJ
+The basic idea of ensemble classification is to train a set of base classifiers and then to combine their prediction using some combination scheme in a hope that the combined prediction will be better than the separated predictions.
+Empirically, ensemble learners tend to outperform their base members due to the significantly better generalization ability of the ensemble.
+This is because ensemble learners can reduce the the bias and variance problems of the base learning algorithms \cite{dietterich2002ensemble}.
+In the following, we describe the most popular ensemble methods: Bagging, Boosting and Random Forests.
 

### 2016-12-09 paper.tex
Added main steps of the methodology
@amorag please check :)

--- 2016-12-08 paper.tex
@@
 %sales, and not the precise number. 
-An important task when publishing a new book is determining an accurate number 
-of copies to be printed. Doing both an under- or an overestimation will lead to financial losses.
-In this paper, we address the problem of predicting total sales using cost-sensitive ensemble methods.
-% Antonio - explain briefly what are them
-These can be used as reliable decision-aid tools for publishers, as a part of the final stages of the editorial process. 
-Thus, a real dataset including the complete sales data for books published in Spain across several years has been used to compute the prediction models.
-% Antonio - extend a bit this with the followed methodology.
-% Explain also the method you are using and why it's an improvement
-% over the previous one - JJ
-We evaluate our approach on the real data collected by a Spanish publishing company.
+% Antonio - it is true, but how can we justify this, JJ?
+% I guess that precision is relative in this kind of methods, since the publisher is not going to print exactly '237' books due to it is the output of a regression method.
+Instead, there could be a range of books to be printed (as a standard) related with an expected 'low', 'medium', 'high' or 'very high' amount of sales.
+% Moreover, I guess that the classification output, considering four classes would work better (more precisely and close to reality) than regression.
+% What do you think?
+An important task when publishing a new book is determining the number 
+of copies to be printed, since doing both a (dramatic) under- or overestimation will lead to important financial losses.
+In this paper, we transform this problem into a classification one, defining different sales levels i.e. classes. 
+The obtained results will be easier to interpret by publishers than other black-box techniques, 
+so these methods can be used as reliable decision-aid tools for publishers, to be considered in their decision as a part of the final stages of the editorial process.
+
+The problem of predicting these levels has been addressed applying cost-sensitive ensemble methods.
+% Antonio - explain briefly what are them  and  the followed methodology.
+In order to do so, a real dataset collected by a Spanish publishing company, including the complete sales data for books published in Spain across several years, has been used to design and evaluate the prediction models.
+% Explain also the method you are using and why it's an improvement over the previous one - JJ
 Results show that %\emph{EXPLAIN THE RESULTS OBTAINED}.
@@
 
-Reliable sales prediction can enhance the whole production process for different companies involved in manufacturing, marketing and trading.
+Reliable sales prediction can enhance the whole production process for different 
+companies involved in manufacturing, marketing and trading.
+Moreover, in some real-world cases, such as consumer electronics, fashion products and books, new products are presented/launched every season; thus, accurate sales forecasting models could help in marketing campaigns for instance.
 
-Specifically, focusing in the publishing process of a new book, deciding the optimal {\em
-  print run}, i.e. the number of copies to be printed and delivered to
-bookstores, is a very challenging problem, that is why it is extremely
+Specifically, focusing in the publishing process of a new book, deciding the optimal {\em  print run}, i.e.
+the number of copies to be printed and delivered to bookstores, is a very challenging problem.
+Thus, it is extremely
 important to develop accurate predictive models which could forecast
 the future sales a new book will achieve, in order to optimise
-production schedules: to improve the publishing company profits and to
-minimise losses \cite{Zhao2001}, due both to the excess or to the
-scarcity of units. 
+production schedules \cite{Fildes2010,Saeed2008,Zhao2001}, to improve the publishing company profits and to minimise losses, due both to the excess or to the scarcity of units. 
 %I would eliminate this paragraph. We have it on the other one.
-Since, according to the results reported in \cite{Fildes2010,Saeed2008}, reducing the error in estimated sales leads to an enhancement of the whole production process.
+%Since, according to the results reported in \cite{Fildes2010,Saeed2008}, reducing the error in estimated sales leads to an enhancement of the whole production process.
+% Antonio - I agree. Removed
 
-Usually the prediction of book sales has been generally based on experts' experience.
-They analyse data about sales and, taking into account their knowledge of the industry, the production process, and their perception about trends, and take decisions on the production and publication process.
-However, this process might be tedious, especially when the amount of data is 
-quite large. Moreover, the results are not robust, since different experts can reach different predictions from the same dataset \cite{Sanders1994}.
+Traditionally the prediction of book sales has been generally based on experts' experience.
+They analyse data about sales and, taking into account their knowledge of the industry, the production issues, and their perception about trends, take decisions on the production and publication processes.
+However, this procedure might be tedious, especially when the amount of data is 
+quite large. Moreover, the results are not robust, since different experts could come to different predictions from the same dataset \cite{Sanders1994}.
 
-%\textbf{UNDER CONSTRUCTION}
-% Antonio - I remove the ';)' because I want to check the parentheses
-% correspondence and it breaks it. :P
-% Use comments for non-text comments. Like under construction - JJ
+% TODO: UNDER CONSTRUCTION
 % Define level of sales before you use it here. Is it the actual
@@
 % sales - JJ 
-To make the print run as close as possible to the actual level of sales, it is 
-essential to have an estimation of those sales. 
-In this sense, this paper continues our previous work on book sales prediction 
-\cite{Castillo2016books} in which the main factors influencing sales where 
-analyzed in order to create a tool that the publisher can use to decide how many 
-books should be printed.
-In that paper, several regression methods were applied to estimate sales for new launched books using a real dataset of book sales related to the Spanish market, provided by the Spanish publishing company Trevenque Editorial S.L.\footnote{\tt http://editorial.trevenque.es}
+% Antonio - done in a paragraph below
+It is also possible to use any kind of decision-aid tool, such as estimating or predictive models.
+These should be able to compute an accurate number of expected sales which can help the publisher (expert) to take the optimal decision.
+Thus, in our previous work \cite{Castillo2016books}, the main factors influencing sales where analyzed in order to create that kind of tool.
+In that paper, several regression methods were applied to estimate sales for new launched books using a real dataset of book sales related to the Spanish market, provided by the Spanish publishing company Trevenque Editorial S.L.\footnote{\tt http://editorial.trevenque.es}.
 
-However, since finding adequate forecasting techniques and selecting the best method 
-to use represents also a problem, we propose configuring complex models based on
-ensembles \cite{Qiu2014} in order to determine the actual 
-level of sales a new book will achieve.
-Moreover, since publishers need models to explain obtained predictions, and 
-`black box' forecasting methods may not be suitable, using these ensemble 
-models publishers will be able to combine their expert knowledge about the 
-market with the created forecasting models in order to get a reliable estimation 
-of book sales level.
+% Antonio - this is themotivation/justification of the present work. Please all chek it. ;D
+However, the complexity of those models, even if they yielded a decision tree might be a flaw for publishers when they must work with them in real scenarios, since the leaves of those trees are complicated regression formulae.
+In addition, the estimated number despite being accurate according to the experiments, might not be very reliable for these experts, in the sense that most of them would prefer to deal with categorical variables to include in their own `prediction formulae'.
 
-% Antonio - We must remark that this approach is based in classification rather than regression, which is based on levels of sales (classes) instead of on numerical results.
-These will be easily 'explained' or justified for a (human) publisher.
-% Previous work also presented the results in an intelligible way, since it offered decision trees as the last output, but they include regression computation in the leaves.
-Here the models/outputs will be easily interpreted.
+Thus, having in mind `the human factor' of the print-run decision process, in this paper we have addressed the problem from a new perspective.
+We have defined, with the help of an expert, different \textit{levels or ranges of sales}, composing different incremental categories: \textit{Low, Medium, High} and \textit{Very High}.
+Then, these have been considered as classes, so the given dataset has been labelled according to them, and the problem has been faced as a classification one.
 
+Moreover, handling the problem as a classification task let us to emphasize on the ranges which could be more `critical', e.g.
+the most profitable books (High and Very High categories).
+Thus, we can penalize more the misclassification of these categories and, consequently, this tool will perform a better identification of successful books than our previous approach \cite{Castillo2016books}.
+% which will be definitely very interesting for publishers.
+
+In order to solve this problem, in this work we propose configuring complex models based on ensembles \cite{Qiu2014} in order to determine the actual level of sales a new book will achieve.
+% Antonio - justify why ensembles have been chosen instead of other classification approaches: accuracy, perform, easier to interpret, faster, ...
+Another advantage of the proposed approach is that they are easier to interpret than `black box' forecasting methods, such as regression techniques.
+So, using these ensemble methods, publishers will be able to combine their expert knowledge about the
+market with the obtained models in order to get a reliable estimation 
+on book sales level. Moreover, as the output will be just a class, they will be able to understand and justify better their decision.
+
+% Antonio: TODO - explain how are we going to demonstrate the value of this proposal and how are we going to prove that it is better than our previous approach...
+Will it 'better' or just 'different' and also valid as a decision tool?
+Will we count with an expert to compare them?
+Maybe JJ could be the Expert?
+:D
+
+% Antonio: TODO - rewrite with the final structure
 The rest of this paper is structured as follows: 
@@
 
-Sales prediction is an important problem that can improve the quality of business 
-strategy for different companies. 
-Traditionally, sales prediction problems have been solved using advaced methods 
-such as regression models \cite{Papalexopoulos1990}, neural networks \cite{Yoo1999}, 
-fuzzy systems \cite{Mastorocostas2001}, or mixture of methods \cite{Chang2006715,Meulstee2008,ChiJie2012}.
+%Sales prediction is an important problem that can improve the quality of business strategy for different companies. 
+% Antonio - not needed to mention this again in this section. Maybe we can move it to the introduction. ;)
+Traditionally, sales prediction problems have been solved using advanced mathematical and machine learning-based methods
+% Antonio - why are they 'advanced'?
+such as regression models \cite{Papalexopoulos1990}, neural networks \cite{Yoo1999}, fuzzy systems \cite{Mastorocostas2001}, or mixture of methods \cite{Chang2006715,Meulstee2008,ChiJie2012}.
 
-The most used technique to tackle sales forecasting problems is time-series prediction methods
-\cite{Chu2003,Brown1959,Winters1960,Box1969,Papalexopoulos1990,KayacanUK10},
-however the correctness of the problem data strongly affects the predictions obtained.
+In this line, the most used techniques to tackle sales forecasting problems have been time-series prediction
+\cite{Chu2003,Brown1959,Winters1960,Box1969,Papalexopoulos1990}. %,KayacanUK10}. % Antonio - the last reference doesn't exist
+However these methods are strongly dependent on problem data, so the obtained predictions are highly affected by their correctness.
 Moreover, this kind of methods are based on using historical data to make time series.
-However, in the case of new products sales prediction (such as the issue of new books), 
-there is no available historical sales data \cite{ChingChin2010}, 
+However, in the case of new products sales prediction (such as the issue of new books), there is no available historical sales data \cite{ChingChin2010},
 and only pre-sales data are available \cite{FaderHardie2005,Madsen2008}, 
 i.e. variables known before the product is on sale. 
+% Antonio - We should rewrite this, since a similar sentence was a weak asseveration in previous paper.
+The proposed methodology also uses historical data to infer the print-run of new books, so, why is this a problem for Time Series and it is useful for the proposed methods?
+:/
 
-Not only the lack of historical data makes this a complex problem, but also the fact 
-that several variables (seasonality, promotions, or fashions) might influence predictions
+Not only the lack of historical data makes this a complex problem, but also the fact that several `external' variables (seasonality, promotions, or fashions) might influence predictions
 \cite{Lapide1999,Thomassey2012,Xia2012,SThomassey2014,ChernWSF15}.
+% Antonio - choose just a couple of references to justify this. ;)
 
 Due to the difficulty this problem represents when forecasting sales of new 
-products, some authors have proposed using different data mining methods, such as
-data clustering and fuzzy neural networks \cite{Chang2009}  or
-extreme learning machine with adaptive metrics of inputs \cite{Xia2012}.
-In this sense, several authors have proposed using ensemble of models for sales forecasting, 
-as in \cite{ChiJie2012}, where a hybrid forecasting model integrates ensemble 
-empirical model decomposition and extreme learning machine to develop an effective 
-forecasting model for computer products sales.
-Also, Meulstee et al. \cite{Meulstee2008} developed an ensemble learning approach 
-for better handling of seasonal changes and fluctuations in consumer demands,
-while Chang et al. \cite{Chang2006715} integrated a fuzzy logic controller 
-and artificial neural network for sales forecasting in printed circuit board industry.
+products, some authors have proposed using different data mining methods, such as data clustering and fuzzy neural networks \cite{Chang2009} or extreme learning machine with adaptive metrics of inputs \cite{Xia2012}.
+In this line, several authors have applied the ensemble of models for sales forecasting, 
+% Antonio - briefly clarify what is an ensemble
+as it is done in \cite{ChiJie2012}, where a hybrid forecasting method integrates ensemble empirical model decomposition and extreme learning machine 
+% Antonio - learning machine or machine learning?
+% Anyway, what does it mean?
+to develop an effective forecasting model for computer products sales.
+Also, Meulstee et al.
+\cite{Meulstee2008} developed an ensemble learning approach for better handling of seasonal changes and fluctuations in consumer demands, whereas Chang et al.
+\cite{Chang2006715} integrated a fuzzy logic controller and an artificial neural network for sales forecasting in printed circuit board industry.
+
 Another authors have faced the problem of sales forecasting in textile-apparel 
 fashion industry (a very similar issue to the new book publishing problem) 
-using a clustering method together with decision trees, as in \cite{SThomassey2014},  or
-a forecasting method based on extreme machine learning with adaptive metrics of inputs \cite{Xia2012}.
+using a clustering method together with decision trees, as in \cite{SThomassey2014},  or a forecasting method based on extreme machine learning with adaptive metrics of inputs \cite{Xia2012}.
+% Antonio - comment this last paper
 
-% TODO
+Ching et al. \cite{ChingChin2010} used a decision-support system to classify new 
+products (tea, cosmetics and soft drink) based on their sales patterns, assuming 
+that products in the same class would follow a similar sales pattern. 
+In any case, the proposed system can not deal with qualitative data related to the products. 
+In this paper, several classification-based approaches have been implemented and tested, also considering categorical data.
+
+%Finally, in those problems where historical data are available, authors have 
+%proposed to apply classical time series forecasting methods.
+% Antonio - we said previously more or less that Time Series Prediction is not recommended
+
+In \cite{Chang2009} a hybrid model integrating K-Means and fuzzy neural networks 
+to forecast the future sales of a printed circuit board is proposed.
+% Antonio - compare it with our work
+Recent works propose to take advantage of the information extracted from online reviews, such as in \cite{ChernWSF15} where it is conducted an analysis on historical data throughout online reviews, reviewer characteristics, and review influences; in order to understand how electronic `word-of-mouth' influences product sales.
+Similar researches took advantage of the information published on specialized 
+blogs \cite{Moon2010ICSSSM,Moon2010ICEC}, confirming there is a relationship between the number of blog references and the book sales.
+Therefore, different sales patterns have been observed by analysing books in series, i.e.
+the first book published takes the longest period to achieve every single sales scale, while the second book takes the second longest period, and so on.
+In these cases, sales forecasting problems can be carried out thanks to a big 
+amount of online reviews and historical data.
+% Antonio - compare these works and findings with our current work
+
+This paper continues our previous work on the prediction of sales of a new product for which no historical data are available, and where the classical forecasting methods based on time-series are not adequate \cite{Castillo2016books}.
+In that paper the main factors influencing sales where
+analyzed in order to create a tool, based on several regression methods, that the publisher can use to decide how many books should be printed.
+
+However, in this paper we address the problem of new book sales prediction using cost-sensitive ensemble methods, defining with the help of an expert different \textit{levels or ranges of sales} in order to compose different incremental categories or classes.
 
@@
 \label{sec:methodology}
+
+\begin{itemize}
+\item Data preparation:
+
+\item Select best base classifier:
+
+\item Select best ensemble classifier:
+
+\item Perform cost-sensitive analysis with best ensemble classifiers:
+
+\item Evaluation and comparison:
+
+\end{itemize}
 
@@
 weak) base learners, meaning that small changes in the training data lead to big changes in the developed models.
+Besides the selection of the base classifier, the effect of the number of iterations is experimented in RF, Bagging and AdaBoost as shown in Figures \ref{fig:PerformanceRF}, \ref{fig:PerformanceBagging} and \ref{fig:PerformanceAdaboost}, respectively.
+Highest prediction rates are obtained at 60 iterations.
+The best obtained results for these ensemble classifiers are shown in Table \ref{table:ensemble_classifiers}.
+It can be seen that all ensemble classifiers achieved higher accuracy rates compared to J48 from the previous stage, achieving around 74\% with approximately 4\% improvement.
+Inspecting the obtained results for VH class, we can notice that although the recall of the VH hasn't improved much compared to J48, the precision has remarkably increased from 74\% to 81.6\%, 80.8\% and 79.3\% for RF, Adaboost and Bagging, respectively.
+For the H class, there was an improvement for both measurements, recall and precision.
+RF and Adaboost achieved approximately 68\% and 67\% for recall and precision, while Bagging achieved 67\% and 66\%, respectively.
+Also, it can be noticed that there is an improvement in general for the other classes, M and L.
 

### 2016-12-20 paper.tex
Important concern to justify the paper
Have a look @JJ @pacastillo @7ossam81
SotA revised

--- 2016-12-09 paper.tex
@@
 %sales, and not the precise number. 
+% Antonio - it is true, but how can we justify this, JJ?
+% I guess that precision is relative in this kind of methods, since the publisher is not going to print exactly '237' books due to it is the output of a regression method.
+Instead, there could be a range of books to be printed (as a standard) related with an expected 'low', 'medium', 'high' or 'very high' amount of sales.
+% Moreover, I guess that the classification output, considering four classes would work better (more precisely and close to reality) than regression.
+% What do you think?
 An important task when publishing a new book is determining an accurate number 
@@
 
-Sales prediction is an important problem that can improve the quality of business 
-strategy for different companies. 
-Traditionally, sales prediction problems have been solved using advaced methods 
-such as regression models \cite{Papalexopoulos1990}, neural networks \cite{Yoo1999}, 
-fuzzy systems \cite{Mastorocostas2001}, or mixture of methods \cite{Chang2006715,Meulstee2008,ChiJie2012}.
+%Sales prediction is an important problem that can improve the quality of business strategy for different companies. 
+% Antonio - not needed to mention this again in this section. Maybe we can move it to the introduction. ;)
+Traditionally, sales prediction problems have been solved using advanced mathematical and machine learning-based methods
+% Antonio - why are they 'advanced'?
+such as regression models \cite{Papalexopoulos1990}, neural networks \cite{Yoo1999}, fuzzy systems \cite{Mastorocostas2001}, or mixture of methods \cite{Chang2006715,Meulstee2008,ChiJie2012}.
 
-The most used technique to tackle sales forecasting problems is time-series prediction methods
-\cite{Chu2003,Brown1959,Winters1960,Box1969,Papalexopoulos1990,KayacanUK10},
-however the correctness of the problem data strongly affects the predictions obtained.
+In this line, the most used techniques to tackle sales forecasting problems have been time-series prediction
+\cite{Chu2003,Brown1959,Winters1960,Box1969,Papalexopoulos1990,KayacanUK10}.
+% Antonio - the last reference doesn't exist
+However these methods are strongly dependent on problem data, so the obtained predictions are highly affected by their correctness.
 Moreover, this kind of methods are based on using historical data to make time series.
-However, in the case of new products sales prediction (such as the issue of new books), 
-there is no available historical sales data \cite{ChingChin2010}, 
+However, in the case of new products sales prediction (such as the issue of new books), there is no available historical sales data \cite{ChingChin2010},
 and only pre-sales data are available \cite{FaderHardie2005,Madsen2008}, 
 i.e. variables known before the product is on sale. 
+% Antonio - We should rewrite this, since a similar sentence was a weak asseveration in previous paper.
+The proposed methodology also uses historical data to infer the print-run of new books, so, why is this a problem for Time Series and it is useful for the proposed methods?
+:/
 
-Not only the lack of historical data makes this a complex problem, but also the fact 
-that several variables (seasonality, promotions, or fashions) might influence predictions
+Not only the lack of historical data makes this a complex problem, but also the fact that several `external' variables (seasonality, promotions, or fashions) might influence predictions
 \cite{Lapide1999,Thomassey2012,Xia2012,SThomassey2014,ChernWSF15}.
+% Antonio - choose just a couple of references to justify this. ;)
 
 Due to the difficulty this problem represents when forecasting sales of new 
-products, some authors have proposed using different data mining methods, such as
-data clustering and fuzzy neural networks \cite{Chang2009}  or
-extreme learning machine with adaptive metrics of inputs \cite{Xia2012}.
-In this sense, several authors have proposed using ensemble of models for sales forecasting, 
-as in \cite{ChiJie2012}, where a hybrid forecasting model integrates ensemble 
-empirical model decomposition and extreme learning machine to develop an effective 
-forecasting model for computer products sales.
-Also, Meulstee et al. \cite{Meulstee2008} developed an ensemble learning approach 
-for better handling of seasonal changes and fluctuations in consumer demands,
-while Chang et al. \cite{Chang2006715} integrated a fuzzy logic controller 
-and artificial neural network for sales forecasting in printed circuit board industry.
+products, some authors have proposed using different data mining methods, such as data clustering and fuzzy neural networks \cite{Chang2009} or extreme learning machine with adaptive metrics of inputs \cite{Xia2012}.
+In this line, several authors have applied the ensemble of models for sales forecasting, 
+% Antonio - briefly clarify what is an ensemble
+as it is done in \cite{ChiJie2012}, where a hybrid forecasting method integrates ensemble empirical model decomposition and extreme learning machine 
+% Antonio - learning machine or machine learning?
+% Anyway, what does it mean?
+to develop an effective forecasting model for computer products sales.
+Also, Meulstee et al.
+\cite{Meulstee2008} developed an ensemble learning approach for better handling of seasonal changes and fluctuations in consumer demands, whereas Chang et al.
+\cite{Chang2006715} integrated a fuzzy logic controller and an artificial neural network for sales forecasting in printed circuit board industry.
+
 Another authors have faced the problem of sales forecasting in textile-apparel 
 fashion industry (a very similar issue to the new book publishing problem) 
-using a clustering method together with decision trees, as in \cite{SThomassey2014},  or
-a forecasting method based on extreme machine learning with adaptive metrics 
-of inputs \cite{Xia2012}.
-Ching et al. \cite{ChingChin2010} use a decision-support system to classify new 
+using a clustering method together with decision trees, as in \cite{SThomassey2014},  or a forecasting method based on extreme machine learning with adaptive metrics of inputs \cite{Xia2012}.
+% Antonio - comment this last paper
+
+Ching et al. \cite{ChingChin2010} used a decision-support system to classify new 
 products (tea, cosmetics and soft drink) based on their sales patterns, assuming 
 that products in the same class would follow a similar sales pattern. 
-In any case, the proposed system can not deal with qualitative 
-data related to the products.
+In any case, the proposed system can not deal with qualitative data related to the products. 
+In this paper, several classification-based approaches have been implemented and tested, also considering categorical data.
 
-Finally, in those problems where historical data are available, authors have 
-proposed applying classical time series forecasting methods.
+%Finally, in those problems where historical data are available, authors have 
+%proposed to apply classical time series forecasting methods.
+% Antonio - we said previously more or less that Time Series Prediction is not recommended
+
 In \cite{Chang2009} a hybrid model integrating K-Means and fuzzy neural networks 
 to forecast the future sales of a printed circuit board is proposed.
-Recent works propose take advantage of information extracted from online reviews, 
-such as in \cite{ChernWSF15} where an analysis on historical data throughout online 
-reviews, reviewer characteristics, and review influences to understand how 
-electronic `word-of-mouth' influences product sales is presented.
-Similar works propose take advantage of information published on specialized 
-blogs \cite{Moon2010ICSSSM,Moon2010ICEC}, having confirmed relationships between 
-the number of blog references and book sales, at the time that different sales 
-patterns have been observed by analysing books in series (the first book published 
-takes the longest period to achieve every single sales scale, while the second book 
-takes the second longest period, and so on).
+% Antonio - compare it with our work
+Recent works propose to take advantage of the information extracted from online reviews, such as in \cite{ChernWSF15} where it is conducted an analysis on historical data throughout online reviews, reviewer characteristics, and review influences; in order to understand how electronic `word-of-mouth' influences product sales.
+Similar researches took advantage of the information published on specialized 
+blogs \cite{Moon2010ICSSSM,Moon2010ICEC}, confirming there is a relationship between the number of blog references and the book sales.
+Therefore, different sales patterns have been observed by analysing books in series, i.e.
+the first book published takes the longest period to achieve every single sales scale, while the second book takes the second longest period, and so on.
 In these cases, sales forecasting problems can be carried out thanks to a big 
 amount of online reviews and historical data.
+% Antonio - compare these works and findings with our current work
 
-This paper continues our work on the prediction of sales of a new product for 
-which no historical data are available, and where the classical forecasting methods 
-based on time-series are not adequate.
-In this sense, in \cite{Castillo2016books} the main factors influencing sales where 
-analyzed in order to create a tool, based on several regression methods, that the 
-publisher can use to decide how many books should be printed.
+This paper continues our previous work on the prediction of sales of a new product for which no historical data are available, and where the classical forecasting methods based on time-series are not adequate \cite{Castillo2016books}.
+In that paper the main factors influencing sales where
+analyzed in order to create a tool, based on several regression methods, that the publisher can use to decide how many books should be printed.
 
-In this paper we address the problem of new book sales prediction using cost-sensitive ensemble methods.
+However, in this paper we address the problem of new book sales prediction using cost-sensitive ensemble methods.
 % TODO: complete this paragraph.
+% Antonio - say why we continue the previous work (what wer the flaws), how are we continuing it, wat we expect to improve, the objective contribution, etc
 

### 2016-12-21 paper.tex
Introduction revised
Following JJ's suggestions.
Please @JJ, @pacastillo @7ossam81 check it. ;D

--- 2016-12-09 paper.tex
@@
 of copies to be printed, since doing both a (dramatic) under- or overestimation will lead to important financial losses.
-In this paper, we transform this problem into a classification one, defining different sales levels i.e. classes. 
-The obtained results will be easier to interpret by publishers than other black-box techniques, 
-so these methods can be used as reliable decision-aid tools for publishers, to be considered in their decision as a part of the final stages of the editorial process.
-
-The problem of predicting these levels has been addressed applying cost-sensitive ensemble methods.
-% Antonio - explain briefly what are them  and  the followed methodology.
-In order to do so, a real dataset collected by a Spanish publishing company, including the complete sales data for books published in Spain across several years, has been used to design and evaluate the prediction models.
-% Explain also the method you are using and why it's an improvement over the previous one - JJ
+In this paper, we transform this problem into a classification one, defining different sales levels. Then, we address the problem of predicting these levels  applying cost-sensitive ensemble methods.
+% Antonio - explain briefly what are them
+These can be used as reliable decision-aid tools for publishers, as a part of the final stages of the editorial process. 
+Thus, a real dataset including the complete sales data for books published in Spain across several years has been used to compute the prediction models.
+% Antonio - extend a bit this with the followed methodology.
+% Explain also the method you are using and why it's an improvement
+% over the previous one - JJ
+We evaluate our approach on the real data collected by a Spanish publishing company.
 Results show that %\emph{EXPLAIN THE RESULTS OBTAINED}.
@@
 the future sales a new book will achieve, in order to optimise
-production schedules \cite{Fildes2010,Saeed2008,Zhao2001}, to improve the publishing company profits and to minimise losses, due both to the excess or to the scarcity of units. 
+production schedules \cite{Fildes2010,Saeed2008,Zhao2001}: to improve the publishing company profits and to minimise losses, due both to the excess or to the scarcity of units. 
 %I would eliminate this paragraph. We have it on the other one.
@@
 
-Thus, having in mind `the human factor' of the print-run decision process, in this paper we have addressed the problem from a new perspective.
-We have defined, with the help of an expert, different \textit{levels or ranges of sales}, composing different incremental categories: \textit{Low, Medium, High} and \textit{Very High}.
+Thus, having in mind `the human factor' of the print-run decision process, in this paper we have addressed the problem from another perspective.
+We have defined, with the help of an expert, different \textit{levels or ranges of sales}, composing different incremental categories: low, medium, high and very high.
 Then, these have been considered as classes, so the given dataset has been labelled according to them, and the problem has been faced as a classification one.
 
-Moreover, handling the problem as a classification task let us to emphasize on the ranges which could be more `critical', e.g.
-the most profitable books (High and Very High categories).
-Thus, we can penalize more the misclassification of these categories and, consequently, this tool will perform a better identification of successful books than our previous approach \cite{Castillo2016books}.
-% which will be definitely very interesting for publishers.
-
-In order to solve this problem, in this work we propose configuring complex models based on ensembles \cite{Qiu2014} in order to determine the actual level of sales a new book will achieve.
+In order to solve it, in this work we propose configuring complex models based on ensembles \cite{Qiu2014} in order to determine the actual level of sales a new book will achieve.
 % Antonio - justify why ensembles have been chosen instead of other classification approaches: accuracy, perform, easier to interpret, faster, ...
-Another advantage of the proposed approach is that they are easier to interpret than `black box' forecasting methods, such as regression techniques.
+Another advantage is they are easier to interpret than `black box' forecasting methods, such as regression techniques.
 So, using these ensemble methods, publishers will be able to combine their expert knowledge about the
@@
 In this line, the most used techniques to tackle sales forecasting problems have been time-series prediction
-\cite{Chu2003,Brown1959,Winters1960,Box1969,Papalexopoulos1990}. %,KayacanUK10}. % Antonio - the last reference doesn't exist
+\cite{Chu2003,Brown1959,Winters1960,Box1969,Papalexopoulos1990,KayacanUK10}.
+% Antonio - the last reference doesn't exist
 However these methods are strongly dependent on problem data, so the obtained predictions are highly affected by their correctness.
@@
 
-However, in this paper we address the problem of new book sales prediction using cost-sensitive ensemble methods, defining with the help of an expert different \textit{levels or ranges of sales} in order to compose different incremental categories or classes.
+However, in this paper we address the problem of new book sales prediction using cost-sensitive ensemble methods.
+% TODO: complete this paragraph.
+% Antonio - say why we continue the previous work (what wer the flaws), how are we continuing it, wat we expect to improve, the objective contribution, etc
 
@@
 \label{sec:methodology}
-
-\begin{itemize}
-\item Data preparation:
-
-\item Select best base classifier:
-
-\item Select best ensemble classifier:
-
-\item Perform cost-sensitive analysis with best ensemble classifiers:
-
-\item Evaluation and comparison:
-
-\end{itemize}
 
@@
 weak) base learners, meaning that small changes in the training data lead to big changes in the developed models.
-Besides the selection of the base classifier, the effect of the number of iterations is experimented in RF, Bagging and AdaBoost as shown in Figures \ref{fig:PerformanceRF}, \ref{fig:PerformanceBagging} and \ref{fig:PerformanceAdaboost}, respectively.
-Highest prediction rates are obtained at 60 iterations.
-The best obtained results for these ensemble classifiers are shown in Table \ref{table:ensemble_classifiers}.
-It can be seen that all ensemble classifiers achieved higher accuracy rates compared to J48 from the previous stage, achieving around 74\% with approximately 4\% improvement.
-Inspecting the obtained results for VH class, we can notice that although the recall of the VH hasn't improved much compared to J48, the precision has remarkably increased from 74\% to 81.6\%, 80.8\% and 79.3\% for RF, Adaboost and Bagging, respectively.
-For the H class, there was an improvement for both measurements, recall and precision.
-RF and Adaboost achieved approximately 68\% and 67\% for recall and precision, while Bagging achieved 67\% and 66\%, respectively.
-Also, it can be noticed that there is an improvement in general for the other classes, M and L.
 

### 2016-12-28 paper.tex
Adding Hossam's point to the motivation
Please, check it @7ossam81  @JJ and @pacastillo

@@
 of copies to be printed, since doing both a (dramatic) under- or overestimation will lead to important financial losses.
-In this paper, we transform this problem into a classification one, defining different sales levels. Then, we address the problem of predicting these levels  applying cost-sensitive ensemble methods.
+In this paper, we transform this problem into a classification one, defining different sales levels i.e.
+classes.
+The obtained results will be easier to interpret by publishers than other black-box techniques, so they will consider them in their decision process.
+The problem of predicting these levels has been addressed applying cost-sensitive ensemble methods.
 % Antonio - explain briefly what are them
@@
 Thus, having in mind `the human factor' of the print-run decision process, in this paper we have addressed the problem from another perspective.
-We have defined, with the help of an expert, different \textit{levels or ranges of sales}, composing different incremental categories: low, medium, high and very high.
+We have defined, with the help of an expert, different \textit{levels or ranges of sales}, composing different incremental categories: \textit{Low, Medium, High} and \textit{Very High}.
 Then, these have been considered as classes, so the given dataset has been labelled according to them, and the problem has been faced as a classification one.
+
+Moreover, handling the problem as a classification task let us to give more emphasize on the ranges which could be more `critical', e.g.
+the most profitable books (High and Very High categories).
+Thus, we can penalize more the misclassification of these categories and, consequently, this tool will perform a better identification of successful books than our previous approach.
+% which will be definitely very interesting for publishers.
 

### 2016-12-29 paper.tex
improving some sentences in the abstract

@@
 of copies to be printed, since doing both a (dramatic) under- or overestimation will lead to important financial losses.
-In this paper, we transform this problem into a classification one, defining different sales levels i.e.
-classes.
-The obtained results will be easier to interpret by publishers than other black-box techniques, so they will consider them in their decision process.
+In this paper, we transform this problem into a classification one, defining different sales levels i.e. classes. 
+The obtained results will be easier to interpret by publishers than other black-box techniques, 
+so these methods can be used as reliable decision-aid tools for publishers, to be considered in their decision as a part of the final stages of the editorial process.
+
 The problem of predicting these levels has been addressed applying cost-sensitive ensemble methods.
-% Antonio - explain briefly what are them
-These can be used as reliable decision-aid tools for publishers, as a part of the final stages of the editorial process. 
-Thus, a real dataset including the complete sales data for books published in Spain across several years has been used to compute the prediction models.
-% Antonio - extend a bit this with the followed methodology.
-% Explain also the method you are using and why it's an improvement
-% over the previous one - JJ
-We evaluate our approach on the real data collected by a Spanish publishing company.
+% Antonio - explain briefly what are them  and  the followed methodology.
+In order to do so, a real dataset collected by a Spanish publishing company, including the complete sales data for books published in Spain across several years, has been used to design and evaluate the prediction models.
+% Explain also the method you are using and why it's an improvement over the previous one - JJ
 Results show that %\emph{EXPLAIN THE RESULTS OBTAINED}.

### 2016-12-29 paper.tex
improving some sentences in the Introduction and State of the Art

@@
 the future sales a new book will achieve, in order to optimise
-production schedules \cite{Fildes2010,Saeed2008,Zhao2001}: to improve the publishing company profits and to minimise losses, due both to the excess or to the scarcity of units. 
+production schedules \cite{Fildes2010,Saeed2008,Zhao2001}, to improve the publishing company profits and to minimise losses, due both to the excess or to the scarcity of units. 
 %I would eliminate this paragraph. We have it on the other one.
@@
 
-Thus, having in mind `the human factor' of the print-run decision process, in this paper we have addressed the problem from another perspective.
+Thus, having in mind `the human factor' of the print-run decision process, in this paper we have addressed the problem from a new perspective.
 We have defined, with the help of an expert, different \textit{levels or ranges of sales}, composing different incremental categories: \textit{Low, Medium, High} and \textit{Very High}.
@@
 
-Moreover, handling the problem as a classification task let us to give more emphasize on the ranges which could be more `critical', e.g.
+Moreover, handling the problem as a classification task let us to emphasize on the ranges which could be more `critical', e.g.
 the most profitable books (High and Very High categories).
-Thus, we can penalize more the misclassification of these categories and, consequently, this tool will perform a better identification of successful books than our previous approach.
+Thus, we can penalize more the misclassification of these categories and, consequently, this tool will perform a better identification of successful books than our previous approach \cite{Castillo2016books}.
 % which will be definitely very interesting for publishers.
 
-In order to solve it, in this work we propose configuring complex models based on ensembles \cite{Qiu2014} in order to determine the actual level of sales a new book will achieve.
+In order to solve this problem, in this work we propose configuring complex models based on ensembles \cite{Qiu2014} in order to determine the actual level of sales a new book will achieve.
 % Antonio - justify why ensembles have been chosen instead of other classification approaches: accuracy, perform, easier to interpret, faster, ...
-Another advantage is they are easier to interpret than `black box' forecasting methods, such as regression techniques.
+Another advantage of the proposed approach is that they are easier to interpret than `black box' forecasting methods, such as regression techniques.
 So, using these ensemble methods, publishers will be able to combine their expert knowledge about the
@@
 In this line, the most used techniques to tackle sales forecasting problems have been time-series prediction
-\cite{Chu2003,Brown1959,Winters1960,Box1969,Papalexopoulos1990,KayacanUK10}.
-% Antonio - the last reference doesn't exist
+\cite{Chu2003,Brown1959,Winters1960,Box1969,Papalexopoulos1990}. %,KayacanUK10}. % Antonio - the last reference doesn't exist
 However these methods are strongly dependent on problem data, so the obtained predictions are highly affected by their correctness.
@@
 
-However, in this paper we address the problem of new book sales prediction using cost-sensitive ensemble methods.
-% TODO: complete this paragraph.
-% Antonio - say why we continue the previous work (what wer the flaws), how are we continuing it, wat we expect to improve, the objective contribution, etc
+However, in this paper we address the problem of new book sales prediction using cost-sensitive ensemble methods, defining with the help of an expert different \textit{levels or ranges of sales} in order to compose different incremental categories or classes.
 

### 2017-03-13 paper.tex
include several sections, as subsections, inside the methodology section
Added three costs matrices

@@
 \usepackage{url}
+\usepackage{multirow}
 
@@
 \label{sec:methodology}
+
+% maybe the following sections should be included inside the Methodology section, as subsections.
+
+\begin{itemize}
+\item Data preparation:
+
+\item Select best base classifier:
+
+\item Select best ensemble classifier:
+
+\item Perform cost-sensitive analysis with best ensemble classifiers:
+
+\item Evaluation and comparison:
+
+\end{itemize}
 
@@
 
+\begin{table}
+\caption{Cost matrices for three different scenarios}
+\centering{}%
+\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|}
+\hline 
+\multicolumn{2}{|c|}{} & \multicolumn{14}{c|}{Actual}\tabularnewline
+\hline 
+\multicolumn{2}{|c|}{} & \multicolumn{4}{c|}{Cost matrix 1} & \multirow{6}{*}{} & \multicolumn{4}{c|}{Cost matrix 2} & \multirow{6}{*}{} & \multicolumn{4}{c|}{Cost matrix 3}\tabularnewline
+\cline{1-6} \cline{8-11} \cline{13-16} 
+\multicolumn{2}{|c|}{} & L & M & H & VH &  & L & M & H & VH &  & L & M & H & VH\tabularnewline
+\cline{1-6} \cline{8-11} \cline{13-16} 
+\multirow{4}{*}{Predicted} & L & 0 & 1 & 2 & 3 &  & 0 & 1 & 2 & 3 &  & 0 & 1 & 2 & 3\tabularnewline
+\cline{2-6} \cline{8-11} \cline{13-16} 
+ & M & 5 & 0 & 1 & 2 &  & 10 & 0 & 1 & 2 &  & 15 & 0 & 1 & 2\tabularnewline
+\cline{2-6} \cline{8-11} \cline{13-16} 
+ & H & 10 & 5 & 0 & 1 &  & 20 & 10 & 0 & 1 &  & 30 & 15 & 0 & 1\tabularnewline
+\cline{2-6} \cline{8-11} \cline{13-16} 
+ & VH & 15 & 10 & 5 & 0 &  & 30 & 20 & 10 & 0 &  & 45 & 30 & 15 & 0\tabularnewline
+\hline 
+\end{tabular}
+\end{table}
+
 %*******************************************************************************

### 2017-03-27 paper.tex
Revision of the State of the Art

@@
 \ead{hossam.faris@ju.edu.jo}
-\author[ugrtstc]{Antonio M. Mora}
-\ead{amorag@geneura.ugr.es}
+\author[ugratc]{Antonio M. Mora}
+\ead{amorag@ugr.es}
 \author[ugratc]{Pedro A. Castillo}
@@
 The University of Jordan, Amman, Jordan}
-\address[ugrtstc]{Department of Signal Theory, Telematics and Communications, ETSIIT and CITIC \\
-University of Granada, Granada, Spain}
+%\address[ugratc]{Department of Signal Theory, Telematics and Communications, ETSIIT and CITIC \\
+%University of Granada, Granada, Spain}
 \address[ugratc]{Department of Computer Architecture and Computer Technology, ETSIIT and CITIC \\
@@
 However these methods are strongly dependent on problem data, so the obtained predictions are highly affected by their correctness.
-Moreover, this kind of methods are based on using historical data to make time series.
-However, in the case of new products sales prediction (such as the issue of new books), there is no available historical sales data \cite{ChingChin2010},
-and only pre-sales data are available \cite{FaderHardie2005,Madsen2008}, 
+Moreover, this kind of methods are based on using historical data about an article to make time series.
+However, in the case of new products sales prediction (such as the issue of new books), there is no available historical sales data for that product \cite{ChingChin2010}, and only pre-sales data can be considered \cite{FaderHardie2005,Madsen2008},
 i.e. variables known before the product is on sale.
-% Antonio - We should rewrite this, since a similar sentence was a weak asseveration in previous paper.
-The proposed methodology also uses historical data to infer the print-run of new books, so, why is this a problem for Time Series and it is useful for the proposed methods?
-:/
 
@@
 Due to the difficulty this problem represents when forecasting sales of new 
-products, some authors have proposed using different data mining methods, such as data clustering and fuzzy neural networks \cite{Chang2009} or extreme learning machine with adaptive metrics of inputs \cite{Xia2012}.
-In this line, several authors have applied the ensemble of models for sales forecasting, 
-% Antonio - briefly clarify what is an ensemble
-as it is done in \cite{ChiJie2012}, where a hybrid forecasting method integrates ensemble empirical model decomposition and extreme learning machine 
-% Antonio - learning machine or machine learning?
-% Anyway, what does it mean?
-to develop an effective forecasting model for computer products sales.
+products, some authors have proposed using different data mining methods, such as data clustering and fuzzy neural networks \cite{Chang2009} or extreme learning machine (ELM) - a feedforward neural network in which the weights are just computed once and not changed - with adaptive metrics of inputs \cite{Xia2012}.
+
+In this line, several authors have applied the \textit{ensemble} (or combination) of models for sales forecasting, as it is done in \cite{ChiJie2012}, where a hybrid forecasting method integrates ensemble empirical model decomposition and ELM to develop an effective forecasting model for computer products sales.
 Also, Meulstee et al.
@@
 
-Another authors have faced the problem of sales forecasting in textile-apparel 
-fashion industry (a very similar issue to the new book publishing problem) 
-using a clustering method together with decision trees, as in \cite{SThomassey2014},  or a forecasting method based on extreme machine learning with adaptive metrics of inputs \cite{Xia2012}.
+Other authors have faced the problem of sales forecasting in textile-apparel 
+fashion industry - a very similar issue to the new book publishing problem - 
+using a clustering method together with decision trees, as in \cite{SThomassey2014}, or a forecasting method based on ELM with adaptive metrics of inputs \cite{Xia2012}.
 % Antonio - comment this last paper
@@
 In any case, the proposed system can not deal with qualitative data related to the products. 
-In this paper, several classification-based approaches have been implemented and tested, also considering categorical data.
+In this paper, however, several classification-based approaches have been implemented and tested, also considering categorical data.
 
@@
 
-However, in this paper we address the problem of new book sales prediction using cost-sensitive ensemble methods, defining with the help of an expert different \textit{levels or ranges of sales} in order to compose different incremental categories or classes.
+However, in this paper we address the problem of new book sales prediction considering a different approach.
+We transform this problem into a classification one defining, with the help of an expert, different \textit{levels or ranges of sales} in order to compose different incremental categories or classes.
+Then we apply cost-sensitive ensemble methods in order to build effective models to determine the category (regarding sales) to which a new book would belong, yielding an useful approximation for the publisher.
 
@@
 The discretization of the volume of sales was conducted by an expert in the domain of editorial management business, who defined the four categories.
+% Antonio - TODO: It would be great if we could justify... At least, the expert (JJ :P) could write a sentence clarifying his decision for these ranges.
 
@@
 We can notice that most of the investigated books are categorized as Low and Medium levels forming 26.8\% and 36.4\% of the dataset, respectively.
-High volumes of sold books that range from 300 up to 1000 are categorized as High volume of sales and form 24\% of the dataset.
+High volumes of sold books that range from 301 up to 1000 are categorized as High volume of sales and form 24\% of the dataset.
 On the other hand, books that achieved more than 1000 sold copies are categorized as Very High and they form around 12.8\% of the dataset.
@@
 \hline 
-Category & Range of total sales & Count & Ratio\tabularnewline
+Category & Range of total sales & Number of books & Ratio\tabularnewline
 \hline 
@@
 \hline 
-High & 300-1000 & 1460 & 24\%\tabularnewline
+High & 301-1000 & 1460 & 24\%\tabularnewline
 \hline 

### 2017-03-27 paper.tex
Added description of book categories
But there are multiple grammar edits, too. Grammar has to be revised
_very_ extensively before it is submitted.

@@
 so these methods can be used as reliable decision-aid tools for publishers, to be considered in their decision as a part of the final stages of the editorial process.
-
+% paragraphs in the abstract is not a good idea.
 The problem of predicting these levels has been addressed applying cost-sensitive ensemble methods.
@@
 % Antonio - to refine later
-Book sales forecasting \sep Decision-aid models \sep Feature selection \sep Classification \sep Ensemble methods
+Book sales forecasting \sep Decision-aid models \sep Feature selection
+\sep Classification \sep Ensemble methods %why commas _and_ CAPS? - JJ
 \end{keyword}
@@
 
-Moreover, handling the problem as a classification task let us to emphasize on the ranges which could be more `critical', e.g.
-the most profitable books (High and Very High categories).
+Moreover, handling the problem as a classification task let us to
+emphasize on the ranges which could be more `critical', e.g. the most
+profitable books (High and Very High categories). % You have used
+                                % italics for this before but no
+                                % emphasis now. You have to unify
+                                % typography - JJ
 Thus, we can penalize more the misclassification of these categories and, consequently, this tool will perform a better identification of successful books than our previous approach \cite{Castillo2016books}.
@@
 
-In this line, the most used techniques to tackle sales forecasting problems have been time-series prediction
+In this line of work, the most widely used techniques to tackle sales forecasting problems have been time-series prediction
 \cite{Chu2003,Brown1959,Winters1960,Box1969,Papalexopoulos1990}. %,KayacanUK10}. % Antonio - the last reference doesn't exist
@@
 Recent works propose to take advantage of the information extracted from online reviews, such as in \cite{ChernWSF15} where it is conducted an analysis on historical data throughout online reviews, reviewer characteristics, and review influences; in order to understand how electronic `word-of-mouth' influences product sales.
-Similar researches took advantage of the information published on specialized 
+Similar research efforts took advantage of the information published
+on specialized  %please revise 
 blogs \cite{Moon2010ICSSSM,Moon2010ICEC}, confirming there is a relationship between the number of blog references and the book sales.
@@
 % Antonio - compare these works and findings with our current work
+
+% There is no clear narrative here. State of the art must show the
+% progression in this kind of work and how different levels of success
+% have been achieved via different methods. You have to hint that what
+% we are using here, sales levels, is going to be better than
+% predicting sales via a regression model, for instance - JJ
 
@@
 
-The obtained dataset contains collected information about 6083 different books produced by 209 publishers.
-Each book or pattern in the dataset is represented by 10 features as shown in Table \ref{tabla:params_pre_sales}.
-
+The obtained dataset contains collected information about 6083
+different books produced by 209 publishers. Each book or pattern in
+the dataset is represented by 10 features, listed in Table
+\ref{tabla:params_pre_sales}. 
+%
 \begin{table*}
@@
 
-The output variable which is related to the total amount of sales is a categorical variable which represent the level of the quantity sold for a given book.
-Thus, four categories have been considered to represent these levels: \textit{Low (L)}, \textit{Medium (M)}, \textit{High (H)}, and \textit{Very High (VH)}.
-Table \ref{table:freq} shows the ranges of total sales that correspond to each category along with the number of sold books that fall in.
-The discretization of the volume of sales was conducted by an expert in the domain of editorial management business, who defined the four categories.
-% Antonio - TODO: It would be great if we could justify... At least, the expert (JJ :P) could write a sentence clarifying his decision for these ranges.
+The output variable related to the total amount of sales is a
+categorical variable which represent the level of the quantity sold
+for a given book. We have defined four categories to
+represent these levels: \textit{Low (L)}, \textit{Medium (M)},
+\textit{High (H)}, and \textit{Very High (VH)}. Table \ref{table:freq}
+shows the ranges of total sales that correspond to each category along
+with the number of sold books that fall in. The discretization of the
+volume of sales was conducted by an expert in the domain of editorial
+management business, who defined the four categories. They are also
+adapted to the Spanish market. The first level, 60, corresponds to the
+first quartile in the book sales distribution: 25\% of books sell less
+than 60 copies. The second has been established at the typical print
+run in the Spanish market, which is 300 copies, including not only
+books for sale, but also books sent as a gift, to display or for
+reviewers. 1000 books would be considered a decently selling book with
+several print runs; second print run will depend on how fast the first
+one sales, but could typically be 500 to 1000 new copies. Anything
+selling more than 1000 copies will sell extremely well, with only 60
+books reaching more than 5000 physical copies sold in the data set we
+used. These sales levels will have to be adjusted to particular
+markets using the same methodology we have used here, although a good
+rule of thumb would be, after examining the initial data set and the
+distribution of sales among different books, to choose the 4 quartiles
+or 3 terciles and split the top one giving the ``very high'' category
+to the books in the top decile.
 
-Table \ref{table:freq} reveal more information about the nature of the dataset.
-We can notice that most of the investigated books are categorized as Low and Medium levels forming 26.8\% and 36.4\% of the dataset, respectively.
-High volumes of sold books that range from 301 up to 1000 are categorized as High volume of sales and form 24\% of the dataset.
-On the other hand, books that achieved more than 1000 sold copies are categorized as Very High and they form around 12.8\% of the dataset.
-Our focus in this study is to identify the more profitable categories which are High and Very High.
-However, since the latter category is much smaller than the other ones, we can describe our dataset as imbalanced dataset which makes the problem of identifying this category harder and more challenging.
+Table \ref{table:freq} reveal more information about the nature of the
+dataset. Please note that most of the investigated books are
+categorized as Low and Medium %once again, unify typography
+levels forming 26.8\% and 36.4\% of the dataset, respectively. High
+volumes of sold books that range from 301 up to 1000 are categorized
+as High volume of sales and form 24\% of the dataset. On the other
+hand, books that achieved more than 1000 sold copies are categorized
+as Very High and they form around 12.8\% of the dataset. Our focus in
+this study is to identify the more profitable categories which are
+High and Very High. However, since the latter category is much smaller
+than the other ones, we can describe our dataset as imbalanced which
+makes the problem of identifying this category harder and more
+challenging.
 

### 2017-10-11 paper.tex
Added description for cost-sensitive methods

@@
 
+%------------------------ COST SENSITIVE CLASSIFICATION ------------------------
+\subsection{Cost sensitive classification}
+\label{subsec:cost_classification}
+
+This method adjusts the classifier's prediction output by changing its probability threshold which depends on a predefined cost.
+To illustrate the idea of the cost-sensitive classification, the threshold $P$ for a given case can be calculated based on a general cost matrix $C$, where $C$ can be represented as given in Equation \ref{Eq:costMatrix}.
+
+\begin{equation}
+C=\left[\begin{array}{cc}
+0 & \lambda\\
+\mu & 0
+\end{array}\right]
+\label{Eq:costMatrix}
+\end{equation}
+
+Based on the matrix $C$, the threshold $P$ can be determined using Equation \ref{Eq:costThreshold}.
+
+\begin{equation}
+P=\frac{\mu}{\mu+\lambda}
+\label{Eq:costThreshold}
+\end{equation}
+
+Therefore, $P$ can be used to distinguish between the two classes.
+If the probability classification output of the model is less than the threshold then it classifies as the minority class, otherwise it classifies as a majority class.
+
 %------------------------ COST SENSITIVE LEARNING ------------------------
@@
 
-%------------------------ COST SENSITIVE CLASSIFICATION ------------------------
-\subsection{Cost sensitive classification}
-\label{subsec:cost_classification}
+In this method, a given classification algorithm performs the learning process based on a new version of the dataset, where the instances are re-weighted internally according to some predefined costs.
 

### 2017-11-26 paper.tex
updating Acknowledgements

--- 2017-03-27 paper.tex
@@
 
-This work has been supported in part by projects PreTEL (PRM
-Consultores - Trevenque S.L.), TIN2014-56494-C4-3-P and TEC2015-68752
-(Spanish Ministry of Economy and Competitiveness and FEDER), and
-PROY-PP2015-06 (Plan Propio 2015, funded by the University of Granada,
-Spain).
-% Is still this last grant running?
+This work has been partially funded by projects 
+PreTEL (PRM Consultores - Trevenque S.L.)
+EphemeCH TIN2014-56494-C4-3-P, 
+DeepBio TIN2017-85727-C4-2-P    and 
+TEC2015-68752 
+(Spanish Ministry of Economy and Competitiveness and FEDER).
 
